---
title: "Preparing data for analyses presented in: Intergenerational effects of physical exercise on cognition and brain: a multilevel meta-analysis of mean and variance"
output:
  html_document: default
---


## Step 1 - Loading, checking, cleaning and calculating effect size

### 1. Install and load required packages

```{r setup, echo = FALSE}
# Tidy
 # rm(list=ls())

# Workspace
  knitr::opts_chunk$set(echo = TRUE, include = TRUE)

# Loading packages
 # install.packages("pacman") # install this if you never installed it before
   pacman::p_load(knitr, # knit this markdown
                  readxl, # read Excel files  
                  metafor,
                  dplyr, # transforming data
                  tidyverse, # tidy family to manioulate data
                  matrixcalc, # positive-definite matrix check; first time to install from devtools::install_github('cran/matrixcalc')
                  purrr, # functional programming tools
                  janitor # tabulating overlaps
                 );source('./functions/functions.R')
```


### 2. Dataset


```{r Import and check}
# Import the dataset
  raw_all_traits <- read_excel('./database/all_traits.xlsx', col_names = TRUE)

# Check
  dim(raw_all_traits)
  head(raw_all_traits)
  str(raw_all_traits)
  names(raw_all_traits)
```


### 3. Data preprocessing

```{r Preprocessing }
# Fixing factors (variables) types
 # Locating columns which are numeric
   num_column <- c('year', 'age_manipulation_d', 'age_mating_d', 'n_con_parent', 'n_exp_parent','manipulation_duration', 'response_age_PND', 'exp_mean', 'exp_se', 'exp_n', 'con_mean', 'con_se', 'con_n', 'biological_direction')

 # Turning into numeric
   pos <- lapply(as.list(names(raw_all_traits)), function(x) is_empty(which(str_detect(x, num_column) == T)) == F) %>% unlist
  raw_all_traits[,pos] <- lapply(raw_all_traits[,pos], as.numeric)


 # Locating rest columns which should be factors
   fac_column <- which((unlist(lapply(as.list(names(raw_all_traits)), function(x) ifelse(test = is_empty(which(str_detect(x, num_column) == T)), yes = 'fac_column', no = 'num_column'))) == 'fac_column') == T)

 # Turning into factors
   raw_all_traits[,fac_column] <- lapply(raw_all_traits [,fac_column], as.factor)

# Checking missing data
  dim(raw_all_traits[is.na(raw_all_traits$exp_mean | raw_all_traits$exp_n | raw_all_traits$con_mean | raw_all_traits$con_n), ]) # no records with missing descriptive statistics

# Checking included studies
  length(unique(raw_all_traits$study_ID)) # 52 included studies

# Checking  effect size
  length(unique(raw_all_traits$ES_ID)) #410 unique effect sizes from 410 observations   

# Checking random effects and moderators
 # F0 attributes (random effects)
   tabyl(raw_all_traits, species) # 73 mice and 339 rats
   tabyl(raw_all_traits, strain) # 73 C57BL/6, 23 Sprague-Dawley, 28 Long-Evans, 288 Wistar

 # F0 moderators (fixed effects)
   tabyl(raw_all_traits, F0_sex_exercise) # 340 female of F0 and 72 male of F0
   tabyl(raw_all_traits, manipulation_type) # 90 swimming, 160 treadmill-running and 80 wheel-running, 82 environmental enrichment
   tabyl(raw_all_traits, manipulation_mode) # 250 forced exercise and 162 voluntary exercise
   tabyl(raw_all_traits, manipulation_window) # 111 pre-conception, 205 pregnancy, 78  pre-conception to pregnancy, 18 pre-conception to post-partum

 # F1 attributes (additional moderators)
   tabyl(raw_all_traits, F1_sex_test) # 64 F1 female, 221 F1 male and 127 F1 mixed-sex
   tabyl(raw_all_traits, response_age_life_phase) # 25 prenatal, 64 early postnatal, 224 adolescence, 99 adulthood
 
   # Overlap of moderators and random factors
   tabyl(raw_all_traits, manipulation_type, F0_sex_exercise) 
   tabyl(raw_all_traits, manipulation_mode, F0_sex_exercise) 
   tabyl(raw_all_traits, manipulation_window, F0_sex_exercise) 
   tabyl(raw_all_traits, manipulation_type, F1_sex_test) 
   tabyl(raw_all_traits, manipulation_mode, F1_sex_test) 
   tabyl(raw_all_traits, manipulation_window, F1_sex_test) 
   tabyl(raw_all_traits, manipulation_mode, response_age_life_phase) 

# Pass check
  all_traits <- raw_all_traits
```


### 4. Calculate effect size
Calculate effect size and sampling variance for each pairwise group (exp-control) from included studies
exp = F0 exposed to exercise, con = F0 exposed to sedentary
effect size (sampling variance): lnRR(VlnRR), lnCVR(VlnCVR)

```{r Calculation}
# Computing standard deviations
  all_traits$exp_sd <- all_traits$exp_se*sqrt(all_traits$exp_n)
  all_traits$con_sd <- all_traits$con_se*sqrt(all_traits$con_n)

# Computing effect size and sampling variance
 # lnRR
   lnRR <- with(all_traits, escalc(measure = 'ROM',
                                m1i = exp_mean,
                                m2i = con_mean,
                                sd1i = exp_sd,
                                sd2i = con_sd,
                                n1i = exp_n,
                                n2i = con_n))

 # lnCVR
   lnCVR <- with(all_traits, escalc(measure = 'CVR',
                                m1i = exp_mean,
                                m2i = con_mean,
                                sd1i = exp_sd,
                                sd2i = con_sd,
                                n1i = exp_n,
                                n2i = con_n))
# Flip negative sign
  effect_size <- data.frame(RR = lnRR$yi*all_traits$biological_direction, 
                          VRR = lnRR$vi,
                          CVR = lnCVR$yi, 
                          VCVR = lnCVR$vi) # Because some of the measures are negatively related with neurodevelopment, so we need to flip them

all_traits <- cbind(all_traits, effect_size)

 # lnCV
   #all_traits$exerciselnCV <- Calc.lnCV(Mean = all_traits$exp_mean, SD = all_traits$con_sd, N = all_traits$con_n)
   #all_traits$controllnCV <- Calc.lnCV(Mean = all_traits$con_mean, SD = all_traits$con_sd, N = all_traits$con_n)
   #all_traits$exerciseVlnCV <- Calc.var.lnCV(Mean = all_traits$exp_mean, SD =    all_traits$con_sd, N = all_traits$con_n)
   #all_traits$controlVlnCV <- Calc.var.lnCV(Mean = all_traits$con_mean, SD = all_traits$con_sd, N = all_traits$con_n)


# Quick visual check 
  hist(all_traits$RR, breaks = 100)
  plot(all_traits$RR, 1/all_traits$VRR)
  hist(all_traits$CVR, breaks = 50)
  plot(all_traits$CVR, 1/all_traits$VCVR)

# Visulizing mean-variance relationship
 # Corretion of control group
   plot(log(all_traits$con_mean), log(all_traits$con_sd))
   cor.test(all_traits$con_mean, all_traits$con_sd) # 0.951138 
 # Corretion of experiment group
   plot(log(all_traits$exp_mean), log(all_traits$exp_sd))
   cor.test(all_traits$exp_mean, all_traits$exp_sd) # 9964369 
```



### 5. Spliting dataset
Preparing specific trait catefories

```{r Subsets}
# Check trait types
  tabyl(all_traits, response_type) 
 # 71 neuron count, 24 brain size
 # 60 BDNF, 14 TrkB, 25 VEGF,  14 reelin, 10 GFAP, 8 syptophysin 
 # 11 mitochondrial biogenesis,  9 DNA methylation
 # 29 learning(MWM), 30 memory(MWM), 17 memory(NOR), 32 anxiety(EPM), 58 anxiety(OFT)

# Define trait categories
 # Some traits have similar  biological effect, so we can group them
 # Adding column to group specific trait into four categories: genes (brain growth factors), brain development, behavior (neurobehavior) and others
   grouped_traits <- NA
   
 # Behavior: learning(MWM), memory(MWM), memory(NOR), anxiety(EPM), anxiety(OFT)
   grouped_traits[all_traits$response_type == 'learning(MWM)'|
                  all_traits$response_type == 'memory(MWM)'|
                  all_traits$response_type == 'memory(NOR)'|
                  all_traits$response_type == 'anxiety(EPM)'|
                  all_traits$response_type == 'anxiety(OFT)'] <- c('behavior') 
   
 # Genes: BDNF, TrkB, VEGF, reelin,  GFAP, syptophysin
   grouped_traits[all_traits$response_type == 'BDNF'|
                  all_traits$response_type == 'TrkB'|
                  all_traits$response_type == 'VEGF'|
                  all_traits$response_type == 'reelin'|
                  all_traits$response_type == 'GFAP'|
                  all_traits$response_type == 'syptophysin'] <- c('genes')
   
 # Brain development: neuron count and brain size
   grouped_traits[all_traits$response_type == 'neuron count'|
                 all_traits$response_type == 'brain size'] <- c('brain development')



 # Others: mitochondrial biogenesis, DNA methylation
   grouped_traits[all_traits$response_type == 'mitochondrial biogenesis'|
                 all_traits$response_type == 'DNA methylation'] <- c('others')


all_traits$grouped_traits <- as.factor(grouped_traits)

 # Split into specific trait categories 
   neuron_count <- all_traits[all_traits$response_type == 'neuron count',] # also can use filter() to split: all_traits %>% filter(response_type == 'trait')
   brain_size <- all_traits[all_traits$response_type == 'brain size',]
   BDNF <- all_traits[all_traits$response_type == 'BDNF',]
   TrkB <- all_traits[all_traits$response_type == 'TrkB',]
   VEGF <- all_traits[all_traits$response_type == 'VEGF',]
   reelin <- all_traits[all_traits$response_type == 'reelin',]
   GFAP <- all_traits[all_traits$response_type == 'GFAP',]
   syptophysin <- all_traits[all_traits$response_type == 'syptophysin',]
   mitochondrial_biogenesis <- all_traits[all_traits$response_type == 'mitochondrial biogenesis',]
   DNA_methylation <- all_traits[all_traits$response_type == 'DNA methylation',]
   learning_MWM <- all_traits[all_traits$response_type == 'learning(MWM)',]
   memory_MWM <- all_traits[all_traits$response_type == 'memory(MWM)',] 
   memory_NOR <- all_traits[all_traits$response_type == 'memory(NOR)',]
   anxiety_OFT <- all_traits[all_traits$response_type == 'anxiety(OFT)',]
   anxiety_EPM <- all_traits[all_traits$response_type == 'anxiety(EPM)',]

 # Split into board trait categories
   behavior <- all_traits %>% filter(grouped_traits == 'behavior') 
   genes <- all_traits %>% filter(grouped_traits == 'genes') 
   brain_development <- all_traits %>% filter(grouped_traits == 'brain development') 


 # we are also inverested in the component of behavior, so we divided behavior into cognition and anxiety
  # cognition <- rbind(learning_MWM, memory_MWM, memory_NOR)
  # anxiety <- rbind(anxiety_OFT, anxiety_EPM)



# Pre-processed subsets for study-level correlations among traits
 # The maximum effect size within each study
   group_by(all_traits, study_ID, grouped_traits) %>% summarise(max.RR = max(RR), max.CVR = max(CVR)) -> overlap.max
   overlap.max <- pivot_wider(overlap.max, names_from = grouped_traits, values_from = c('max.RR', 'max.CVR'))


 # The averaged effect size within each study
   group_by(all_traits, study_ID, grouped_traits) %>% summarise(ave.RR = mean(RR), ave.CVR = mean(CVR)) -> overlap.ave
   overlap.ave <- pivot_wider(overlap.ave, names_from = grouped_traits, values_from = c('ave.RR', 'ave.CVR'))


 # The minmum effect size within each study
   group_by(all_traits,study_ID, grouped_traits) %>% summarise(min.RR = min(RR), min.CVR = min(CVR)) -> overlap.min
   overlap.min <- pivot_wider(overlap.min, names_from = grouped_traits, values_from = c('min.RR', 'min.CVR'))
```



         
### 6. Construct variance-covariance matrices

Effect sizes belong to same cohort (shared cluster) are assumed to be nonindependent (correlated). We quantify the nonindependence caused by shared clusters, then we can abate the impact of nonindependence (more reasonable sampling variance). We assume 0.5 correlation for shared traits from the same animal cohort (conservative assumption)

```{r Variance-covariance matrices}
# Variance-covariance matrices for lnRR
 # Specific catefories
   cov_VRR_neuron_count <- make_VCV_matrix(data = neuron_count, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_brain_size <- make_VCV_matrix(data = brain_size, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_BDNF <- make_VCV_matrix(data = BDNF, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_TrkB <- make_VCV_matrix(data = TrkB, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_VEGF <- make_VCV_matrix(data = VEGF, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_reelin <- make_VCV_matrix(data = reelin, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_GFAP <- make_VCV_matrix(data = GFAP, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_syptophysin <- make_VCV_matrix(data = syptophysin, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_mitochondrial_biogenesis <- make_VCV_matrix(data = mitochondrial_biogenesis, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_learning_MWM <- make_VCV_matrix(data = learning_MWM, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
# cov_VRR_DNA_methylation <- make_VCV_matrix(data = DNA_methylation, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5) # no shared clusters in DNA_methylation
   cov_VRR_memory_MWM <- make_VCV_matrix(data = memory_MWM, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_memory_NOR <- make_VCV_matrix(data = memory_NOR, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_anxiety_OFT <- make_VCV_matrix(data = anxiety_OFT, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_anxiety_EPM <- make_VCV_matrix(data = anxiety_EPM, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)

 # Board categories
   cov_VRR_genes <- make_VCV_matrix(data = genes, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_behavior <- make_VCV_matrix(data = behavior, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VRR_brain_development <- make_VCV_matrix(data = brain_development, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)


# Variance-covariance matrices for lnCVR
 # Specific categories
   cov_VCVR_neuron_count <- make_VCV_matrix(data = neuron_count, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_brain_size <- make_VCV_matrix(data = brain_size, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_BDNF <- make_VCV_matrix(data = BDNF, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_TrkB <- make_VCV_matrix(data = TrkB, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_VEGF <- make_VCV_matrix(data = VEGF, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_reelin <- make_VCV_matrix(data = reelin, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_GFAP <- make_VCV_matrix(data = GFAP, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_syptophysin <- make_VCV_matrix(data = syptophysin, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_mitochondrial_biogenesis <- make_VCV_matrix(data = mitochondrial_biogenesis, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_learning_MWM <- make_VCV_matrix(data = learning_MWM, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   # cov_VCVR_DNA_methylation <- make_VCV_matrix(data = DNA_methylation, V = 'VCVRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5) # no shared clusters in DNA_methylation
   cov_VCVR_memory_MWM <- make_VCV_matrix(data = memory_MWM, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_memory_NOR <- make_VCV_matrix(data = memory_NOR, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_anxiety_OFT <- make_VCV_matrix(data = anxiety_OFT, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_anxiety_EPM <- make_VCV_matrix(data = anxiety_EPM, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)

 # Board categories
   cov_VCVR_genes <- make_VCV_matrix(data = genes, V = 'VCVR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_behavior <- make_VCV_matrix(data = behavior, V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)
   cov_VCVR_brain_development <- make_VCV_matrix(data = brain_development , V = 'VRR', cluster = 'cohort_ID', type = 'vcv', obs = 'ES_ID', rho = 0.5)


# Confirming whether matrices are positive definite or not
 # lnRR
   is.positive.definite(cov_VRR_neuron_count) #TRUE
   is.positive.definite(cov_VRR_brain_size) #TRUE
   is.positive.definite(cov_VRR_BDNF) #TRUE
   is.positive.definite(cov_VRR_TrkB) #TRUE
   is.positive.definite(cov_VRR_VEGF) #TRUE
   is.positive.definite(cov_VRR_reelin) #TRUE
   is.positive.definite(cov_VRR_syptophysin) #TRUE
   is.positive.definite(cov_VRR_mitochondrial_biogenesis) #TRUE
   is.positive.definite(cov_VRR_learning_MWM) #TRUE
   is.positive.definite(cov_VRR_memory_MWM) #TRUE
   is.positive.definite(cov_VRR_memory_NOR) #TRUE
   is.positive.definite(cov_VRR_anxiety_OFT) #TRUE
   is.positive.definite(cov_VRR_genes) #TRUE
   is.positive.definite(cov_VRR_behavior) #TRUE
   is.positive.definite(cov_VRR_brain_development) #TRUE

   # lnCVR
   is.positive.definite(cov_VCVR_neuron_count) #TRUE
   is.positive.definite(cov_VCVR_brain_size) #TRUE
   is.positive.definite(cov_VCVR_BDNF) #TRUE
   is.positive.definite(cov_VCVR_TrkB) #TRUE
   is.positive.definite(cov_VCVR_VEGF) #TRUE
   is.positive.definite(cov_VCVR_reelin) #TRUE
   is.positive.definite(cov_VCVR_syptophysin) #TRUE
   is.positive.definite(cov_VCVR_mitochondrial_biogenesis) #TRUE
   is.positive.definite(cov_VCVR_learning_MWM) #TRUE
   is.positive.definite(cov_VCVR_memory_MWM) #TRUE
   is.positive.definite(cov_VCVR_memory_NOR) #TRUE
   is.positive.definite(cov_VCVR_anxiety_OFT) #TRUE
   is.positive.definite(cov_VCVR_genes) #TRUE
   is.positive.definite(cov_VCVR_behavior) #TRUE
   is.positive.definite(cov_VCVR_brain_development) #TRUE
```



### 7. Saving processed data

```{r Saving}
# Processed dataset
  write.csv(neuron_count, file = './database/neuron_count.csv', row.names = F)
  write.csv(brain_size, file = './database/brain_size.csv', row.names = F)
  write.csv(BDNF, file = './database/BDNF.csv', row.names = F)
  write.csv(TrkB, file = './database/TrkB.csv', row.names = F)
  write.csv(VEGF, file = './database/VEGF.csv', row.names = F)
  write.csv(reelin, file = './database/reelin.csv', row.names = F)
  write.csv(GFAP, file = './database/GFAP.csv', row.names = F) 
  write.csv(syptophysin, file = './database/syptophysin.csv', row.names = F) 
  write.csv(mitochondrial_biogenesis, file = './database/mitochondrial_biogenesis.csv', row.names = F) 
  write.csv(DNA_methylation, file = './database/DNA_methylation.csv', row.names = F)
  write.csv(learning_MWM, file = './database/learning_MWM.csv', row.names = F) 
  write.csv(memory_MWM, file = './database/memory_MWM.csv', row.names = F) 
  write.csv(memory_NOR, file = './database/memory_NOR.csv', row.names = F) 
  write.csv(anxiety_OFT, file = './database/anxiety_OFT.csv', row.names = F) 
  write.csv(anxiety_EPM, file = './database/anxiety_EPM.csv', row.names = F) 
  write.csv(genes, file = './database/genes.csv', row.names = F) 
  write.csv(behavior, file = './database/behavior.csv', row.names = F) 
  write.csv(brain_development, file = './database/brain_development.csv', row.names = F)

# Variance-covariance matrices
 # RR
   save(cov_VRR_neuron_count, file = './database/cov_VRR_neuron_count.Rdata')
   save(cov_VRR_brain_size, file = './database/cov_VRR_brain_size.Rdata')
   save(cov_VRR_BDNF, file = './database/cov_VRR_BDNF.Rdata')
   save(cov_VRR_TrkB, file = './database/cov_VRR_TrkB.Rdata')
   save(cov_VRR_VEGF, file = './database/cov_VRR_VEGF.Rdata')
   save(cov_VRR_reelin, file = './database/cov_VRR_reelin.Rdata')
   save(cov_VRR_GFAP, file = './database/cov_VRR_GFAP.Rdata')
   save(cov_VRR_syptophysin, file = './database/cov_VRR_syptophysin.Rdata')
   save(cov_VRR_mitochondrial_biogenesis, file = './database/cov_VRR_mitochondrial_biogenesis.Rdata')
   #save(cov_VRR_DNA_methylation, file = './database/cov_VRR_DNA_methylation.Rdata')
   save(cov_VRR_learning_MWM, file = './database/cov_VRR_learning_MWM.Rdata')
   save(cov_VRR_memory_MWM, file = './database/cov_VRR_memory_MWM.Rdata')
   save(cov_VRR_memory_NOR, file = './database/cov_VRR_memory_NOR.Rdata')
   save(cov_VRR_anxiety_OFT, file = './database/cov_VRR_anxiety_OFT.Rdata')
   save(cov_VRR_anxiety_EPM, file = './database/cov_VRR_anxiety_EPM.Rdata')
   save(cov_VRR_genes, file = './database/cov_VRR_genes.Rdata')
   save(cov_VRR_behavior, file = './database/cov_VRR_behavior.Rdata')
   save(cov_VRR_brain_development, file = './database/cov_VRR_brain_development.Rdata')

 # lnCVR
   save(cov_VCVR_neuron_count, file = './database/cov_VCVR_neuron_count.Rdata')
   
   save(cov_VCVR_brain_size, file = './database/cov_VCVR_brain_size.Rdata')
   save(cov_VCVR_BDNF, file = './database/cov_VCVR_BDNF.Rdata')
   save(cov_VCVR_TrkB, file = './database/cov_VCVR_TrkB.Rdata')
   save(cov_VCVR_VEGF, file = './database/cov_VCVR_VEGF.Rdata')
   save(cov_VCVR_reelin, file = './database/cov_VCVR_reelin.Rdata')
   save(cov_VCVR_GFAP, file = './database/cov_VCVR_GFAP.Rdata')
   save(cov_VCVR_syptophysin, file = './database/cov_VCVR_syptophysin.Rdata')
   save(cov_VCVR_mitochondrial_biogenesis, file = './database/cov_VCVR_mitochondrial_biogenesis.Rdata')
   #save(cov_VRR_DNA_methylation, file = './database/cov_VRR_DNA_methylation.Rdata')
   save(cov_VCVR_learning_MWM, file = './database/cov_VCVR_learning_MWM.Rdata')
   save(cov_VCVR_memory_MWM, file = './database/cov_VCVR_memory_MWM.Rdata')
   save(cov_VCVR_memory_NOR, file = './database/cov_VCVR_memory_NOR.Rdata')
   save(cov_VCVR_anxiety_OFT, file = './database/cov_VCVR_anxiety_OFT.Rdata')
   save(cov_VCVR_anxiety_EPM, file = './database/cov_VCVR_anxiety_EPM.Rdata')
   save(cov_VCVR_genes, file = './database/cov_VCVR_genes.Rdata')
   save(cov_VCVR_behavior, file = './database/cov_VCVR_behavior.Rdata')
   save(cov_VCVR_brain_development, file = './database/cov_VCVR_brain_development.Rdata')


# Pre-processed dataset for study-level correlations
  save(overlap.max, file = './database/overlap.max.Rdata')
  save(overlap.ave, file = './database/overlap.ave.Rdata')
  save(overlap.min, file = './database/overlap.min.Rdata')
```
