---
title: "Models presented in: Intergenerational effects of physical exercise on cognition and brain: a multilevel meta-analysis of mean and variance"
output:
  html_document: default
---


## Step 2 - Running models


### 1. Setup

```{r setup, echo = FALSE, include = FALSE, warning = FALSE}
# Tidy
 # rm(list=ls())

# Workspace
  knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = FALSE)

# Loading packages
  pacman::p_load(metafor, # running models
                 readr, # reading csv files
                 ggplot2, # visualizing
                 dplyr # manipulating data
              )
  
  
   source('./functions/functions.R')
  
# Importing processed datasets
 # Specific categories
   neuron_count <- read.csv(file = './database/neuron_count.csv')
   brain_size <- read.csv(file = './database/brain_size.csv')
   BDNF <- read.csv(file = './database/BDNF.csv')
   TrkB <- read.csv(file = './database/TrkB.csv')
   VEGF <- read.csv(file = './database/VEGF.csv')
   reelin <- read.csv(file = './database/reelin.csv')
   GFAP <- read.csv(file = './database/GFAP.csv')
   syptophysin <- read.csv(file = './database/syptophysin.csv')
   mitochondrial_biogenesis <- read.csv(file = './database/mitochondrial_biogenesis.csv')
   DNA_methylation <- read.csv(file = './database/DNA_methylation.csv')
   learning_MWM <- read.csv(file = './database/learning_MWM.csv')
   memory_MWM <- read.csv(file = './database/memory_MWM.csv')
   memory_NOR <- read.csv(file = './database/memory_NOR.csv')
   anxiety_OFT <- read.csv(file = './database/anxiety_OFT.csv')
   anxiety_EPM <- read.csv(file = './database/anxiety_EPM.csv')
 # Borad categories
   behavior <- read.csv(file = './database/behavior.csv')
   genes <- read.csv(file = './database/genes.csv')
   brain_development <- read.csv(file = './database/brain_development.csv')  


# Importing variance-corvariance matrices
 # VRR
   load(file = './database/cov_VRR_neuron_count.Rdata')
   load(file = './database/cov_VRR_brain_size.Rdata')
   load(file = './database/cov_VRR_BDNF.Rdata')
   load(file = './database/cov_VRR_TrkB.Rdata')
   load(file = './database/cov_VRR_VEGF.Rdata')
   load(file = './database/cov_VRR_reelin.Rdata')
   load(file = './database/cov_VRR_GFAP.Rdata')
   load(file = './database/cov_VRR_syptophysin.Rdata')
   load(file = './database/cov_VRR_mitochondrial_biogenesis.Rdata')
   load(file = './database/cov_VRR_learning_MWM.Rdata')
   load(file = './database/cov_VRR_memory_MWM.Rdata')
   load(file = './database/cov_VRR_memory_NOR.Rdata')
   load(file = './database/cov_VRR_anxiety_OFT.Rdata')
   load(file = './database/cov_VRR_anxiety_EPM.Rdata')
   load(file = './database/cov_VRR_genes.Rdata')
   load(file = './database/cov_VRR_behavior.Rdata')
   load(file = './database/cov_VRR_brain_development.Rdata')

 # VCVR
   load(file = './database/cov_VCVR_neuron_count.Rdata')
   load(file = './database/cov_VCVR_brain_size.Rdata')
   load(file = './database/cov_VCVR_BDNF.Rdata')
   load(file = './database/cov_VCVR_TrkB.Rdata')
   load(file = './database/cov_VCVR_VEGF.Rdata')
   load(file = './database/cov_VCVR_reelin.Rdata')
   load(file = './database/cov_VCVR_GFAP.Rdata')
   load(file = './database/cov_VCVR_syptophysin.Rdata')
   load(file = './database/cov_VCVR_mitochondrial_biogenesis.Rdata')
   load(file = './database/cov_VCVR_learning_MWM.Rdata')
   load(file = './database/cov_VCVR_memory_MWM.Rdata')
   load(file = './database/cov_VCVR_memory_NOR.Rdata')
   load(file = './database/cov_VCVR_anxiety_OFT.Rdata')
   load(file = './database/cov_VCVR_anxiety_EPM.Rdata')
   load(file = './database/cov_VCVR_genes.Rdata')
   load(file = './database/cov_VCVR_behavior.Rdata')
   load(file = './database/cov_VCVR_brain_development.Rdata')
```



### 2. Non-contrast model

#### (i) Intercept-only model


```{r Overall}
#***************************************************************#
#--------------------- Improvement (lnRR) ----------------------#
#***************************************************************#

#--------------------- Separate traits----------------------#

# neuron count
  model1.neuron_count_RR <- with(neuron_count, rma.mv(yi = RR,
                                                      V = cov_VRR_neuron_count,
                                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                      method = 'REML',
                                                      test = 'z'))


# BDNF
  model1.BDNF_RR <- with(BDNF, rma.mv(yi = RR,
                                      V = cov_VRR_BDNF,
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      method = 'REML',
                                      test = 'z'))


# brain_size
  model1.brain_size_RR <- with(brain_size, rma.mv(yi = RR,
                               V = cov_VRR_brain_size,
                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                               method = 'REML',
                               test = 'z'))
# TrkB
  model1.TrkB_RR <- with(TrkB, rma.mv(yi = RR,
                                      V = cov_VRR_TrkB,
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      method = 'REML',
                                      test = 'z'))
# VEGF
  model1.VEGF_RR <- with(VEGF, rma.mv(yi = RR,
                                      V = cov_VRR_VEGF,
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      method = 'REML',
                                      test = 'z'))
# reelin
  model1.reelin_RR <- with(reelin, rma.mv(yi = RR,
                                          V = cov_VRR_reelin,
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          method = 'REML',
                                          test = 'z'))
# GFAP
  model1.GFAP_RR <- with(GFAP, rma.mv(yi = RR,
                                      V = cov_VRR_GFAP,
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      method = 'REML',
                                      test = 'z'))
# syptophysin
  model1.syptophysin_RR <- with(syptophysin, rma.mv(yi = RR,
                                                    V = cov_VRR_syptophysin,
                                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                    method = 'REML',
                                                    test = 'z'))
# mitochondrial_biogenesis
  model1.mitochondrial_biogenesis_RR <- with(mitochondrial_biogenesis, rma.mv(yi = RR,
                                                                              V = cov_VRR_mitochondrial_biogenesis,
                                                                              random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                                              method = 'REML',
                                                                              test = 'z'))

# DNA_methylation 
 # subset is not enough to achieve convergency, so we replace cor-variance matrix and reduce random effect numbers

  model1.DNA_methylation_RR <- with(DNA_methylation, rma.mv(yi = RR,
                                                            V = VRR,
                                                            random = list( ~1|ES_ID),
                                                            method = 'REML',
                                                            test = 'z'))

# learning_MWM
  model1.learning_MWM_RR <- with(learning_MWM, rma.mv(yi = RR,
                                                      V = cov_VRR_learning_MWM,
                                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                      method = 'REML',
                                                      test = 'z'))

# memory_MWM
  model1.memory_MWM_RR <- with(memory_MWM, rma.mv(yi = RR,
                                                  V = cov_VRR_memory_MWM,
                                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                  method = 'REML',
                                                  test = 'z'))
# memory_NOR
  model1.memory_NOR_RR <- with(memory_NOR, rma.mv(yi = RR,
                                                  V = cov_VRR_memory_NOR,
                                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                  method = 'REML',
                                                  test = 'z'))
# anxiety_OFT
  model1.anxiety_OFT_RR <- with(anxiety_OFT, rma.mv(yi = RR,
                                                    V = cov_VRR_anxiety_OFT,
                                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                    method = 'REML',
                                                  test = 'z'))
# anxiety_EPM
model1.anxiety_EPM_RR <- with(anxiety_EPM, rma.mv(yi = RR,
                                                  V = cov_VRR_anxiety_EPM,
                                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                  method = 'REML',
                                                  test = 'z'))

#--------------------- Board traits----------------------#



# brain_development
  model1.brain_development_RR <- with(brain_development, rma.mv(yi = RR,
                                      V = cov_VRR_brain_development,
                                      random = list(~1|response_type, ~1|strain, ~1|study_ID, ~1|ES_ID),
                                      method = 'REML',
                                      test = 'z'))

# genes
model1.genes_RR <- with(genes, rma.mv(yi = RR,
                                      V = cov_VRR_genes,
                                      random = list(~1|response_type, ~1|strain, ~1|study_ID, ~1|ES_ID),
                                      method = 'REML',
                                      test = 'z'))

# behavior
  model1.behavior_RR <- with(behavior, rma.mv(yi = RR,
                                              V = cov_VRR_behavior,
                                              random = list(~1|response_type, ~1|strain, ~1|study_ID, ~1|ES_ID),
                                              method = 'REML',
                                              test = 'z'))




#***************************************************************#
#------------------ Inter-individual differences (lnCVR) -------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model1.neuron_count_CVR <- with(neuron_count, rma.mv(yi = CVR,
                                                       V = cov_VCVR_neuron_count,
                                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                       method = 'REML',
                                                       test = 'z'))


# BDNF
  model1.BDNF_CVR <- with(BDNF, rma.mv(yi = CVR,
                                       V = cov_VCVR_BDNF,
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       method = 'REML',
                                       test = 'z'))


# brain_size
  model1.brain_size_CVR <- with(brain_size, rma.mv(yi = CVR,
                                                   V = cov_VCVR_brain_size,
                                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                   method = 'REML',
                                                   test = 'z'))
# TrkB
  model1.TrkB_CVR <- with(TrkB, rma.mv(yi = CVR,
                                       V = cov_VCVR_TrkB,
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       method = 'REML',
                                       test = 'z'))
# VEGF
  model1.VEGF_CVR <- with(VEGF, rma.mv(yi = CVR,
                                       V = cov_VCVR_VEGF,
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       method = 'REML',
                                       test = 'z'))
# reelin
  model1.reelin_CVR <- with(reelin, rma.mv(yi = CVR,
                                           V = cov_VCVR_reelin,
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           method = 'REML',
                                           test = 'z'))
# GFAP
  model1.GFAP_CVR <- with(GFAP, rma.mv(yi = CVR,
                                       V = cov_VCVR_GFAP,
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       method = 'REML',
                                       test = 'z'))
# syptophysin
  model1.syptophysin_CVR <- with(syptophysin, rma.mv(yi = CVR,
                                                     V = cov_VCVR_syptophysin,
                                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                     method = 'REML',
                                                     test = 'z'))
# mitochondrial_biogenesis
  model1.mitochondrial_biogenesis_CVR <- with(mitochondrial_biogenesis, rma.mv(yi = CVR,
                                                                               V = cov_VCVR_mitochondrial_biogenesis,
                                                                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                                               method = 'REML',
                                                                               test = 'z'))

# DNA_methylation 
 # subset is not enough to achieve convergency, so we replace cor-variance matrix and reduce random effect numbers

  model1.DNA_methylation_CVR <- with(DNA_methylation, rma.mv(yi = CVR,
                                                             V = VCVR,
                                                             random = list( ~1|ES_ID),
                                                             method = 'REML',
                                                             test = 'z'))

# learning_MWM
  model1.learning_MWM_CVR <- with(learning_MWM, rma.mv(yi = CVR,
                                                       V = cov_VCVR_learning_MWM,
                                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                       method = 'REML',
                                                       test = 'z'))

# memory_MWM
  model1.memory_MWM_CVR <- with(memory_MWM, rma.mv(yi = CVR,
                                                   V = VCVR,
                                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                   method = 'REML',
                                                   test = 'z'))
# memory_NOR
model1.memory_NOR_CVR <- with(memory_NOR, rma.mv(yi = CVR,
                                                 V = cov_VCVR_memory_NOR,
                                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                 method = 'REML',
                                                 test = 'z'))
# anxiety_OFT
  model1.anxiety_OFT_CVR <- with(anxiety_OFT, rma.mv(yi = CVR,
                                                   V = cov_VCVR_anxiety_OFT,
                                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                   method = 'REML',
                                                   test = 'z'))
# anxiety_EPM
model1.anxiety_EPM_CVR <- with(anxiety_EPM, rma.mv(yi = CVR,
                                                   V = cov_VCVR_anxiety_EPM,
                                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                   method = 'REML',
                                                   test = 'z'))

#--------------------- Board traits----------------------#



# brain_development
  model1.brain_development_CVR <- with(brain_development, rma.mv(yi = CVR,
                                                                 V = cov_VCVR_brain_development,
                                                                random = list(~1|response_type, ~1|strain, ~1|study_ID, ~1|ES_ID),
                                                                method = 'REML',
                                                                test = 'z'))

# genes
  model1.genes_CVR <- with(genes, rma.mv(yi = CVR,
                                         V = cov_VCVR_genes,
                                         random = list(~1|response_type, ~1|strain, ~1|study_ID, ~1|ES_ID),
                                         method = 'REML',
                                         test = 'z'))

# behavior
  model1.behavior_CVR <- with(behavior, rma.mv(yi = CVR,
                                               V = cov_VCVR_behavior,
                                               random = list(~1|response_type, ~1|strain, ~1|study_ID, ~1|ES_ID),
                                               method = 'REML',
                                               test = 'z'))



# Saving models for overall effect
 # Improvement (lnRR) 
   save(model1.neuron_count_RR, file = './models/model1.neuron_count_RR.Rdata')
   save(model1.brain_size_RR, file = './models/model1.brain_size_RR.Rdata')
   save(model1.BDNF_RR, file = './models/model1.BDNF_RR.Rdata')
   save(model1.TrkB_RR, file = './models/model1.TrkB_RR.Rdata')
   save(model1.VEGF_RR, file = './models/model1.VEGF_RR.Rdata')
   save(model1.reelin_RR, file = './models/model1.reelin_RR.Rdata')
   save(model1.GFAP_RR, file = './models/model1.GFAP_RR.Rdata')
   save(model1.syptophysin_RR, file = './models/model1.syptophysin_RR.Rdata')
   save(model1.mitochondrial_biogenesis_RR, file = './models/model1.mitochondrial_biogenesis_RR.Rdata')
   save(model1.DNA_methylation_RR, file = './models/model1.DNA_methylation_RR.Rdata')
   save(model1.learning_MWM_RR, file = './models/model1.learning_MWM_RR.Rdata')
   save(model1.memory_MWM_RR, file = './models/model1.memory_MWM_RR.Rdata')
   save(model1.anxiety_OFT_RR, file = './models/model1.anxiety_OFT_RR.Rdata')
   save(model1.anxiety_EPM_RR, file = './models/model1.anxiety_EPM_RR.Rdata')
   save(model1.genes_RR, file = './models/model1.genes_RR.Rdata')
   save(model1.behavior_RR, file = './models/model1.behavior_RR.Rdata')
   save(model1.brain_development_RR, file = './models/model1.brain_development_RR.Rdata')

 # Inter-individual differences (lnCVR) 
   save(model1.neuron_count_CVR, file = './models/model1.neuron_count_CVR.Rdata')
   save(model1.brain_size_CVR, file = './models/model1.brain_size_CVR.Rdata')
   save(model1.BDNF_CVR, file = './models/model1.BDNF_CVR.Rdata')
   save(model1.TrkB_CVR, file = './models/model1.TrkB_CVR.Rdata')
   save(model1.VEGF_CVR, file = './models/model1.VEGF_CVR.Rdata')
   save(model1.reelin_CVR, file = './models/model1.reelin_CVR.Rdata')
   save(model1.GFAP_CVR, file = './models/model1.GFAP_CVR.Rdata')
   save(model1.syptophysin_CVR, file = './models/model1.syptophysin_CVR.Rdata')
   save(model1.mitochondrial_biogenesis_CVR, file = './models/model1.mitochondrial_biogenesis_CVR.Rdata')
   save(model1.DNA_methylation_CVR, file = './models/model1.DNA_methylation_CVR.Rdata')
   save(model1.learning_MWM_CVR, file = './models/model1.learning_MWM_CVR.Rdata')
   save(model1.memory_MWM_CVR, file = './models/model1.memory_MWM_CVR.Rdata')
   save(model1.memory_NOR_CVR, file = './models/model1.memory_NOR_CVR.Rdata')
   save(model1.anxiety_OFT_CVR, file = './models/model1.anxiety_OFT_CVR.Rdata')
   save(model1.anxiety_EPM_CVR, file = './models/model1.anxiety_EPM_CVR.Rdata')
   save(model1.genes_CVR, file = './models/model1.genes_CVR.Rdata')
   save(model1.behavior_CVR, file = './models/model1.behavior_CVR.Rdata')
   save(model1.brain_development_CVR, file = './models/model1.brain_development_CVR.Rdata')
```



#### (ii) Univariate regression model - parental sex


```{r parental sex)}
#***************************************************************#
#--------------------- Improvement (lnRR) ----------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model2.neuron_count_RR <- rma.mv(yi = RR, 
                                   V = cov_VRR_neuron_count, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                   data = neuron_count)

# BDNF
  model2.BDNF_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_BDNF, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                           data = BDNF)

# brain_siz
  model2.brain_size_RR <- rma.mv(yi = RR, 
                               V = cov_VRR_brain_size, 
                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                               mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                               data = brain_size)

# TrkB
  model2.TrkB_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_TrkB, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                           data = TrkB)

# VEGF
  model2.VEGF_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_VEGF, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                           data = VEGF)
# reelin
  model2.reelin_RR <- rma.mv(yi = RR, 
                             V = cov_VRR_reelin, 
                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                             mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                             data = reelin)
# GFAP
  model2.GFAP_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_GFAP, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                           data = GFAP)
# syptophysin
  model2.syptophysin_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_syptophysin, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                  data = syptophysin)
# mitochondrial_biogenesis
  model2.mitochondrial_biogenesis_RR <- rma.mv(yi = RR, 
                                               V = cov_VRR_mitochondrial_biogenesis, 
                                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                               mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                               data = mitochondrial_biogenesis)
# DNA_methylation
  model2.DNA_methylation_RR <- rma.mv(yi = RR, 
                                      V = VRR, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                      data = DNA_methylation)
# learning_MWM
  model2.learning_MWM_RR <- rma.mv(yi = RR, 
                                   V = cov_VRR_learning_MWM, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                   data = learning_MWM)
# memory_MWM
model2.memory_MWM_RR <- rma.mv(yi = RR, 
                               V = cov_VRR_memory_MWM, 
                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                               mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                               data = memory_MWM)
# memory_NOR
  model2.memory_NOR_RR <- rma.mv(yi = RR, 
                                 V = VRR, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                 data = memory_NOR)
# anxiety_OFT
  model2.anxiety_OFT_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_anxiety_OFT, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                  data = anxiety_OFT)
# anxiety_EPM
  model2.anxiety_EPM_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_anxiety_EPM, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                  data = anxiety_EPM)


#--------------------- Board traits----------------------#


# brain_development
  model2.brain_development_RR <- rma.mv(yi = RR, 
                                        V = cov_VRR_brain_development, 
                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                        mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                        data = brain_development)

# genes
  model2.genes_RR <- rma.mv(yi = RR, 
                            V = cov_VRR_genes, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                            data = genes)


# behavior
  model2.behavior_RR <- rma.mv(yi = RR, 
                               V = cov_VRR_behavior, 
                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                               mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                               data = behavior)


#***************************************************************#
#------------------ Inter-individual differences (lnCVR) -------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model2.neuron_count_CVR <- rma.mv(yi = CVR, 
                                    V = cov_VCVR_neuron_count, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                    data = neuron_count)

# brain_size
  model2.brain_size_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_brain_size, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                  data = brain_size)

# BDNF
  model2.BDNF_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_BDNF, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                            data = BDNF)

#TrkB
  model2.TrkB_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_TrkB, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                            data = TrkB)
# VEGF
  model2.VEGF_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_VEGF, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                            data = VEGF)
# reelin
  model2.reelin_CVR <- rma.mv(yi = CVR, 
                              V = cov_VCVR_reelin, 
                              random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                              mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                              data = reelin)
# GFAP
  model2.GFAP_CVR <- rma.mv(yi = CVR, 
                            V = VCVR, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                            data = GFAP)
# syptophysin
  model2.syptophysin_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_syptophysin, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                   data = syptophysin)
# mitochondrial_biogenesis
  model2.mitochondrial_biogenesis_CVR <- rma.mv(yi = CVR, 
                                                V = cov_VCVR_mitochondrial_biogenesis, 
                                                random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                                data = mitochondrial_biogenesis)
# DNA_methylation
model2.DNA_methylation_CVR <- rma.mv(yi = CVR, 
                                     V = VCVR, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                     data = DNA_methylation)
# learning_MWM
  model2.learning_MWM_CVR <- rma.mv(yi = CVR, 
                                    V = cov_VCVR_learning_MWM, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                    data = learning_MWM)
# memory_MWM
  model2.memory_MWM_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_memory_MWM, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                  data = memory_MWM)
# memory_NOR
  model2.memory_NOR_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_memory_NOR, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                  data = memory_NOR)
# anxiety_OFT
  model2.anxiety_OFT_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_anxiety_OFT, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                   data = anxiety_OFT)
# anxiety_EPM
  model2.anxiety_EPM_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_anxiety_EPM, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                   data = anxiety_EPM)


#--------------------- Board traits----------------------#		



# brain_development
  model2.brain_development_CVR <- rma.mv(yi = CVR, 
                                         V = cov_VCVR_brain_development, 
                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                         mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                         data = brain_development)


# genes
  model2.genes_CVR <- rma.mv(yi = CVR, 
                             V = cov_VCVR_genes, 
                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                             mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                             data = genes)


# behavior
  model2.behavior_CVR <- rma.mv(yi = CVR, 
                                V = cov_VCVR_behavior, 
                                random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                mod = ~relevel(F0_sex_exercise, ref = 'male') -1, 
                                data = behavior)


# Saving models
 # Improvement (lnRR) 
   save(model2.neuron_count_RR, file = './models/model2.neuron_count_RR.Rdata')
   save(model2.brain_size_RR, file = './models/model2.brain_size_RR.Rdata')
   save(model2.BDNF_RR, file = './models/model2.BDNF_RR.Rdata')
   save(model2.TrkB_RR, file = './models/model2.TrkB_RR.Rdata')
   save(model2.VEGF_RR, file = './models/model2.VEGF_RR.Rdata')
   save(model2.reelin_RR, file = './models/model2.reelin_RR.Rdata')
   save(model2.GFAP_RR, file = './models/model2.GFAP_RR.Rdata')
   save(model2.syptophysin_RR, file = './models/model2.syptophysin_RR.Rdata')
   save(model2.mitochondrial_biogenesis_RR, file = './models/model2.mitochondrial_biogenesis_RR.Rdata')
   save(model2.DNA_methylation_RR, file = './models/model2.DNA_methylation_RR.Rdata')
   save(model2.learning_MWM_RR, file = './models/model2.learning_MWM_RR.Rdata')
   save(model2.memory_MWM_RR, file = './models/model2.memory_MWM_RR.Rdata')
   save(model2.memory_NOR_RR, file = './models/model2.memory_NOR_RR.Rdata')
   save(model2.anxiety_OFT_RR, file = './models/model2.anxiety_OFT_RR.Rdata')
   save(model2.anxiety_EPM_RR, file = './models/model2.anxiety_EPM_RR.Rdata')
   save(model2.genes_RR, file = './models/model2.genes_RR.Rdata')
   save(model2.behavior_RR, file = './models/model2.behavior_RR.Rdata')
   save(model2.brain_development_RR, file = './models/model2.brain_development_RR.Rdata')

 # Inter-individual differences (lnCVR) 
   save(model2.neuron_count_CVR, file = './models/model2.neuron_count_CVR.Rdata')
   save(model2.brain_size_CVR, file = './models/model2.brain_size_CVR.Rdata')
   save(model2.BDNF_CVR, file = './models/model2.BDNF_CVR.Rdata')
   save(model2.TrkB_CVR, file = './models/model2.TrkB_CVR.Rdata')
   save(model2.VEGF_CVR, file = './models/model2.VEGF_CVR.Rdata')
   save(model2.reelin_CVR, file = './models/model2.reelin_CVR.Rdata')
   save(model2.GFAP_CVR, file = './models/model2.GFAP_CVR.Rdata')
   save(model2.syptophysin_CVR, file = './models/model2.syptophysin_CVR.Rdata')
   save(model2.mitochondrial_biogenesis_CVR, file = './models/model2.mitochondrial_biogenesis_CVR.Rdata')
   save(model2.DNA_methylation_CVR, file = './models/model2.DNA_methylation_CVR.Rdata')
   save(model2.learning_MWM_CVR, file = './models/model2.learning_MWM_CVR.Rdata')
   save(model2.memory_MWM_CVR, file = './models/model2.memory_MWM_CVR.Rdata')
   save(model2.memory_NOR_CVR, file = './models/model2.memory_NOR_CVR.Rdata')
  save(model2.anxiety_OFT_CVR, file = './models/model2.anxiety_OFT_CVR.Rdata')
  save(model2.anxiety_EPM_CVR, file = './models/model2.anxiety_EPM_CVR.Rdata')
  save(model2.behavior_CVR, file = './models/model2.behavior_CVR.Rdata')
  save(model2.brain_development_CVR, file = './models/model2.brain_development_CVR.Rdata')
```


#### (iii) Univariate regression model - offspring sex

```{r offspring sex}
#***************************************************************#
#--------------------- Improvement (lnRR) ----------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model3.neuron_count_RR <- rma.mv(yi = RR, 
                                   V = cov_VRR_neuron_count, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                   data = neuron_count)

# brain_size
  model3.brain_size_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_brain_size, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                 data = brain_size)

# BDNF
  model3.BDNF_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_BDNF, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                           data = BDNF)


# TrkB
  model3.TrkB_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_TrkB, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(F1_sex_test, ref = 'male') -1,  # no  female F1
                           data = TrkB)
# VEGF
  model3.VEGF_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_VEGF, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                           data = VEGF)
# reelin
  model3.reelin_RR <- rma.mv(yi = RR, 
                             V = cov_VRR_reelin, 
                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                             mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                             data = reelin)

# GFAP
  model3.GFAP_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_GFAP, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(F1_sex_test, ref = 'male') -1, # no  female F1
                           data = GFAP)
# syptophysin
  model3.syptophysin_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_syptophysin, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F1_sex_test, ref = 'male') -1, # no  female F1
                                  data = syptophysin)
# mitochondrial_biogenesis
  model3.mitochondrial_biogenesis_RR <- rma.mv(yi = RR, 
                                               V = cov_VRR_mitochondrial_biogenesis, 
                                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                               mod = ~relevel(F1_sex_test, ref = 'male') -1, # no  female F1
                                               data = mitochondrial_biogenesis)
# DNA_methylation
  model3.DNA_methylation_RR <- rma.mv(yi = RR, 
                                      V = VRR, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~relevel(F1_sex_test, ref = 'male') -1, # no  female F1
                                      data = DNA_methylation)
# learning_MWM
  model3.learning_MWM_RR <- rma.mv(yi = RR, 
                                   V = cov_VRR_learning_MWM, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                   data = learning_MWM)
# memory_MWM
  model3.memory_MWM_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_memory_MWM, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                 data = memory_MWM)
# memory_NOR
  model3.memory_NOR_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_memory_NOR, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                 data = memory_NOR)
# anxiety_OFT
  model3.anxiety_OFT_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_anxiety_OFT, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                  data = anxiety_OFT)
# anxiety_EPM
  model3.anxiety_EPM_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_anxiety_EPM, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                  data = anxiety_EPM)

#--------------------- Board traits----------------------#


# brain_development
  model3.brain_development_RR <- rma.mv(yi = RR, 
                                        V = cov_VRR_brain_development, 
                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                        mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                        data = brain_development)

# genes
  model3.genes_RR <- rma.mv(yi = RR, 
                            V = cov_VRR_genes, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                            data = genes)

# behavior
  model3.behavior_RR <- rma.mv(yi = RR, 
                               V = cov_VRR_behavior, 
                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                               mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                               data = behavior)
  

#***************************************************************#
#------------------ Inter-individual differences (lnCVR) -------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model3.neuron_count_CVR <- rma.mv(yi = CVR, 
                                    V = cov_VCVR_neuron_count, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                    data = neuron_count)

# brain_size
model3.brain_size_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_brain_size, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                  data = brain_size)

# BDNF
  model3.BDNF_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_BDNF, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                            data = BDNF)

# TrkB
  model3.TrkB_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_TrkB, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                            data = TrkB)
# VEGF
  model3.VEGF_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_VEGF, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                            data = VEGF)
# reelin
  model3.reelin_CVR <- rma.mv(yi = CVR, 
                              V = cov_VCVR_reelin, 
                              random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                              mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                              data = reelin)
# GFAP
  model3.GFAP_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_GFAP, 
                            random = list(~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                            data = GFAP)
# syptophysin
  model3.syptophysin_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_syptophysin, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                   data = syptophysin)
# mitochondrial_biogenesis
  model3.mitochondrial_biogenesis_CVR <- rma.mv(yi = CVR, 
                                                V = cov_VCVR_mitochondrial_biogenesis, 
                                                random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                                data = mitochondrial_biogenesis)
# DNA_methylation
  model3.DNA_methylation_CVR <- rma.mv(yi = CVR, 
                                       V = VCVR, 
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                       data = DNA_methylation)
# learning_MWM
  model3.learning_MWM_CVR <- rma.mv(yi = CVR, 
                                    V = cov_VCVR_learning_MWM, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                    data = learning_MWM)
# memory_MWM
  model3.memory_MWM_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_memory_MWM, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                  data = memory_MWM)
# memory_NOR
  model3.memory_NOR_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_memory_NOR, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                  data = memory_NOR)
# anxiety_OFT
  model3.anxiety_OFT_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_anxiety_OFT, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                   data = anxiety_OFT)
# anxiety_EPM
  model3.anxiety_EPM_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_anxiety_EPM, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                                   data = anxiety_EPM)

#--------------------- Board traits----------------------#		

# brain_development
  model3.brain_development_CVR <- rma.mv(yi = CVR, 
                                         V = cov_VCVR_brain_development, 
                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                         mod = ~relevel(F1_sex_test, ref = 'male') -1,
                                         data = brain_development)	

# genes
  model3.genes_CVR <- rma.mv(yi = CVR, 
                             V = cov_VCVR_genes, 
                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                             mod = ~relevel(F1_sex_test, ref = 'male') -1, 
                             data = genes)

# behavior
  model3.behavior_CVR <- rma.mv(yi = CVR, 
                                V = cov_VCVR_behavior, 
                                random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                mod = ~relevel(F1_sex_test, ref = 'male') -1,
                                data = behavior)	


# Saving
 # Improvement (lnRR) 
   save(model3.neuron_count_RR, file = './models/model3.neuron_count_RR.Rdata')
   save(model3.brain_size_RR, file = './models/model3.brain_size_RR.Rdata')
   save(model3.BDNF_RR, file = './models/model3.BDNF_RR.Rdata')
   save(model3.TrkB_RR, file = './models/model3.TrkB_RR.Rdata')
   save(model3.VEGF_RR, file = './models/model3.VEGF_RR.Rdata')
   save(model3.reelin_RR, file = './models/model3.reelin_RR.Rdata')
   save(model3.GFAP_RR, file = './models/model3.GFAP_RR.Rdata')
   save(model3.syptophysin_RR, file = './models/model3.syptophysin_RR.Rdata')
   save(model3.mitochondrial_biogenesis_RR, file = './models/model3.mitochondrial_biogenesis_RR.Rdata')
   save(model3.DNA_methylation_RR, file = './models/model3.DNA_methylation_RR.Rdata')
   save(model3.learning_MWM_RR, file = './models/model3.learning_MWM_RR.Rdata')
   save(model3.memory_MWM_RR, file = './models/model3.memory_MWM_RR.Rdata')
   save(model3.memory_NOR_RR, file = './models/model3.memory_NOR_RR.Rdata')
   save(model3.anxiety_OFT_RR, file = './models/model3.anxiety_OFT_RR.Rdata')
   save(model3.anxiety_EPM_RR, file = './models/model3.anxiety_EPM_RR.Rdata')
   save(model3.genes_RR, file = './models/model3.genes_RR.Rdata')
   save(model3.behavior_RR, file = './models/model3.behavior_RR.Rdata')
   save(model3.brain_development_RR, file = './models/model3.brain_development_RR.Rdata')

 # Inter-individual differences (lnCVR) 
   save(model3.neuron_count_CVR, file = './models/model3.neuron_count_CVR.Rdata')
   save(model3.brain_size_CVR, file = './models/model3.brain_size_CVR.Rdata')
   save(model3.BDNF_CVR, file = './models/model3.BDNF_CVR.Rdata')
   save(model3.TrkB_CVR, file = './models/model3.TrkB_CVR.Rdata')
   save(model3.VEGF_CVR, file = './models/model3.VEGF_CVR.Rdata')
   save(model3.reelin_CVR, file = './models/model3.reelin_CVR.Rdata')
   save(model3.GFAP_CVR, file = './models/model3.GFAP_CVR.Rdata')
   save(model3.syptophysin_CVR, file = './models/model3.syptophysin_CVR.Rdata')
   save(model3.mitochondrial_biogenesis_CVR, file = './models/model3.mitochondrial_biogenesis_CVR.Rdata')
   save(model3.DNA_methylation_CVR, file = './models/model3.DNA_methylation_CVR.Rdata')
   save(model3.learning_MWM_CVR, file = './models/model3.learning_MWM_CVR.Rdata')
   save(model3.memory_MWM_CVR, file = './models/model3.memory_MWM_CVR.Rdata')
   save(model3.memory_NOR_CVR, file = './models/model3.memory_NOR_CVR.Rdata')
   save(model3.anxiety_OFT_CVR, file = './models/model3.anxiety_OFT_CVR.Rdata')
   save(model3.anxiety_EPM_CVR, file = './models/model3.anxiety_EPM_CVR.Rdata')
   save(model3.genes_CVR, file = './models/model3.genes_CVR.Rdata')
   save(model3.behavior_CVR, file = './models/model3.behavior_CVR.Rdata')
   save(model3.brain_development_CVR, file = './models/model3.brain_development_CVR.Rdata')
```



#### (iv) Univariate regression mode - exerise mode

```{r exercise mode}
#***************************************************************#
#--------------------- Improvement (lnRR) ----------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model4.neuron_count_RR <- rma.mv(yi = RR, 
                                   V = cov_VRR_neuron_count, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                   data = neuron_count)

# brain_size
  model4.brain_size_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_brain_size, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                 data = brain_size)

# BDNF
  model4.BDNF_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_BDNF, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                           data = BDNF)

# TrkB
  model4.TrkB_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_TrkB, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                           data = TrkB)
# VEGF
  model4.VEGF_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_VEGF, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                           data = VEGF)
# reelin
  model4.reelin_RR <- rma.mv(yi = RR, 
                             V = cov_VRR_reelin, 
                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                             mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                             data = reelin)
# GFAP
  model4.GFAP_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_GFAP, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                           data = GFAP)
# syptophysin
  model4.syptophysin_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_syptophysin, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                  data = syptophysin)
# mitochondrial_biogenesis
  model4.mitochondrial_biogenesis_RR <- rma.mv(yi = RR, 
                                               V = cov_VRR_mitochondrial_biogenesis, 
                                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                               mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                               data = mitochondrial_biogenesis)
  
# DNA_methylation
  model4.DNA_methylation_RR <- rma.mv(yi = RR, 
                                      V = VRR, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                      data = DNA_methylation)
# learning_MWM
  model4.learning_MWM_RR <- rma.mv(yi = RR, 
                                   V = cov_VRR_learning_MWM, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                   data = learning_MWM)
# memory_MWM
  model4.memory_MWM_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_memory_MWM, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                 data = memory_MWM)
# memory_NOR
  model4.memory_NOR_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_memory_NOR, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                 data = memory_NOR)
# anxiety_OFT
  model4.anxiety_OFT_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_anxiety_OFT, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                  data = anxiety_OFT)
# anxiety_EPM
  model4.anxiety_EPM_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_anxiety_EPM, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                  data = anxiety_EPM)

#--------------------- Board traits----------------------#


# brain_development
  model4.brain_development_RR <- rma.mv(yi = RR, 
                                        V = cov_VRR_brain_development, 
                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                        mod = ~relevel(manipulation_mode, ref = 'forced') -1,
                                        data = brain_development)

# genes
  model4.genes_RR <- rma.mv(yi = RR, 
                            V = cov_VRR_genes, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(manipulation_mode, ref = 'forced') -1,
                            data = genes)

# behavior
  model4.behavior_RR <- rma.mv(yi = RR, 
                               V = cov_VRR_behavior, 
                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                               mod = ~relevel(manipulation_mode, ref = 'forced') -1,
                               data = behavior)



#***************************************************************#
#------------- Inter-individual differencesb(lnCVR)-------------# 
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model4.neuron_count_CVR <- rma.mv(yi = CVR, 
                                    V = cov_VCVR_neuron_count, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                    data = neuron_count)

# brain_size
  model4.brain_size_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_brain_size, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                  data = brain_size)

# BDNF
  model4.BDNF_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_BDNF, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                            data = BDNF)

# TrkB
  model4.TrkB_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_TrkB, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                  data = TrkB)
# VEGF
  model4.VEGF_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_VEGF, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                            data = VEGF)
# reelin
  model4.reelin_CVR <- rma.mv(yi = CVR, 
                              V = cov_VCVR_reelin, 
                              random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                              mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                              data = reelin)
# GFAP
  model4.GFAP_CVR <- rma.mv(yi = CVR, 
                                  V = VCVR,#cov_VCVR_GFAP, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                  data = GFAP)
# syptophysin
model4.syptophysin_CVR <- rma.mv(yi = CVR, 
                                 V = cov_VCVR_syptophysin, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                 data = syptophysin)
# mitochondrial_biogenesis
  model4.mitochondrial_biogenesis_CVR <- rma.mv(yi = CVR, 
                                                V = cov_VCVR_mitochondrial_biogenesis, 
                                                random = list(~1|study_ID, ~1|ES_ID),
                                                mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                                data = mitochondrial_biogenesis)
# DNA_methylation
  model4.DNA_methylation_CVR <- rma.mv(yi = CVR, 
                                       V = VCVR, 
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                       data = DNA_methylation)
# learning_MWM
  model4.learning_MWM_CVR <- rma.mv(yi = CVR, 
                                    V = cov_VCVR_learning_MWM, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                    data = learning_MWM)
# memory_MWM
  model4.memory_MWM_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_memory_MWM, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                  data = memory_MWM)
# memory_NOR
  model4.memory_NOR_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_memory_NOR, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                  data = memory_NOR)
# anxiety_OFT
  model4.anxiety_OFT_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_anxiety_OFT, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                   data = anxiety_OFT)
# anxiety_EPM
  model4.anxiety_EPM_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_anxiety_EPM, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(manipulation_mode, ref = 'forced') -1, 
                                   data = anxiety_EPM)

#--------------------- Board traits----------------------#		

# brain_development
  model4.brain_development_CVR <- rma.mv(yi = CVR, 
                                         V = cov_VCVR_brain_development, 
                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                         mod = ~relevel(manipulation_mode, ref = 'forced') -1,
                                         data = brain_development)

# genes
  model4.genes_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_genes, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_mode, ref = 'forced') -1,
                                  data = genes)

# behavior
model4.behavior_CVR <- rma.mv(yi = CVR, 
                              V = cov_VCVR_behavior, 
                              random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                              mod = ~relevel(manipulation_mode, ref = 'forced') -1,
                              data = behavior)



# Saving models
 # Improvement (lnRR) 
   save(model4.neuron_count_RR, file = './models/model4.neuron_count_RR.Rdata')
   save(model4.brain_size_RR, file = './models/model4.brain_size_RR.Rdata')
   save(model4.BDNF_RR, file = './models/model4.BDNF_RR.Rdata')
   save(model4.TrkB_RR, file = './models/model4.TrkB_RR.Rdata')
   save(model4.VEGF_RR, file = './models/model4.VEGF_RR.Rdata')
   save(model4.reelin_RR, file = './models/model4.reelin_RR.Rdata')
   save(model4.GFAP_RR, file = './models/model4.GFAP_RR.Rdata')
   save(model4.syptophysin_RR, file = './models/model4.syptophysin_RR.Rdata')
   save(model4.mitochondrial_biogenesis_RR, file = './models/model4.mitochondrial_biogenesis_RR.Rdata')
   save(model4.DNA_methylation_RR, file = './models/model4.DNA_methylation_RR.Rdata')
   save(model4.learning_MWM_RR, file = './models/model4.learning_MWM_RR.Rdata')
   save(model4.memory_MWM_RR, file = './models/model4.memory_MWM_RR.Rdata')
   save(model4.memory_NOR_RR, file = './models/model4.memory_NOR_RR.Rdata')
   save(model4.anxiety_OFT_RR, file = './models/model4.anxiety_OFT_RR.Rdata')
   save(model4.anxiety_EPM_RR, file = './models/model4.anxiety_EPM_RR.Rdata')
   save(model4.genes_RR, file = './models/model4.genes_RR.Rdata')
   save(model4.behavior_RR, file = './models/model4.behavior_RR.Rdata')
   save(model4.brain_development_RR, file = './models/model4.brain_development_RR.Rdata')

 # Inter-individual differences (lnCVR) 
   save(model4.neuron_count_CVR, file = './models/model4.neuron_count_CVR.Rdata')
   save(model4.brain_size_CVR, file = './models/model4.brain_size_CVR.Rdata')
   save(model4.BDNF_CVR, file = './models/model4.BDNF_CVR.Rdata')
   save(model4.TrkB_CVR, file = './models/model4.TrkB_CVR.Rdata')
   save(model4.VEGF_CVR, file = './models/model4.VEGF_CVR.Rdata')
   save(model4.reelin_CVR, file = './models/model4.reelin_CVR.Rdata')
   save(model4.GFAP_CVR, file = './models/model4.GFAP_CVR.Rdata')
   save(model4.syptophysin_CVR, file = './models/model4.syptophysin_CVR.Rdata')
   save(model4.mitochondrial_biogenesis_CVR, file = './models/model4.mitochondrial_biogenesis_CVR.Rdata')
   save(model4.DNA_methylation_CVR, file = './models/model4.DNA_methylation_CVR.Rdata')
   save(model4.learning_MWM_CVR, file = './models/model4.learning_MWM_CVR.Rdata')
   save(model4.memory_MWM_CVR, file = './models/model4.memory_MWM_CVR.Rdata')
   save(model4.memory_NOR_CVR, file = './models/model4.memory_NOR_CVR.Rdata')
   save(model4.anxiety_OFT_CVR, file = './models/model4.anxiety_OFT_CVR.Rdata')
   save(model4.anxiety_EPM_CVR, file = './models/model4.anxiety_EPM_CVR.Rdata')
   save(model4.genes_CVR, file = './models/model4.genes_CVR.Rdata')
   save(model4.behavior_CVR, file = './models/model4.behavior_CVR.Rdata')
   save(model4.brain_development_CVR, file = './models/model4.brain_development_CVR.Rdata')
```



#### (v) Univariate regression model - exercise timming

```{r exercise timming}
#***************************************************************#
#--------------------- Improvement (lnRR) ----------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model5.neuron_count_RR <- rma.mv(yi = RR, 
                                   V = cov_VRR_neuron_count, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                   data = neuron_count)
# brain_size
  model5.brain_size_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_brain_size, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                 data = brain_size)

# BDNF
  model5.BDNF_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_BDNF, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                           data = BDNF)


# TrkB
  model5.TrkB_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_TrkB, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                           data = TrkB)
# VEGF
  model5.VEGF_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_VEGF, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                           data = VEGF)
# reelin
  model5.reelin_RR <- rma.mv(yi = RR, 
                             V = cov_VRR_reelin, 
                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                             mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                             data = reelin)
# GFAP
  model5.GFAP_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_GFAP, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                           data = GFAP)
# syptophysin
  model5.syptophysin_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_syptophysin, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                  data = syptophysin)

# mitochondrial_biogenesis
  model5.mitochondrial_biogenesis_RR <- rma.mv(yi = RR, 
                                               V = cov_VRR_mitochondrial_biogenesis, 
                                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                               mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                               data = mitochondrial_biogenesis)
  
# DNA_methylation
  model5.DNA_methylation_RR <- rma.mv(yi = RR, 
                                      V = VRR, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                      data = DNA_methylation)
# learning_MWM
  model5.learning_MWM_RR <- rma.mv(yi = RR, 
                                   V = cov_VRR_learning_MWM, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                   data = learning_MWM)
# memory_MWM
  model5.memory_MWM_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_memory_MWM, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                 data = memory_MWM)
# memory_NOR
  model5.memory_NOR_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_memory_NOR, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                 data = memory_NOR)
# anxiety_OFT
  model5.anxiety_OFT_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_anxiety_OFT, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                  data = anxiety_OFT)
# anxiety_EPM
  model5.anxiety_EPM_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_anxiety_EPM, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                  data = anxiety_EPM)

#---------------------  Board traits----------------------#


# brain_development
  model5.brain_development_RR <- rma.mv(yi = RR, 
                                        V = cov_VRR_brain_development, 
                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                        mod = ~relevel(manipulation_window, ref = 'pre-conception') -1,
                                        data = brain_development)


# genes
  model5.genes_RR <- rma.mv(yi = RR, 
                            V = cov_VRR_genes, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(manipulation_window, ref = 'pre-conception') -1,
                            data = genes)


# behavior
  model5.behavior_RR <- rma.mv(yi = RR, 
                               V = cov_VRR_behavior, 
                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                               mod = ~relevel(manipulation_window, ref = 'pre-conception') -1,
                               data = behavior)


#***************************************************************#
#------------------ Inter-individual differences (lnCVR) -------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model5.neuron_count_CVR <- rma.mv(yi = CVR, 
                                    V = cov_VCVR_neuron_count, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                    data = neuron_count)

# BDNF
  model5.BDNF_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_BDNF, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                            data = BDNF)
# brain_size
  model5.brain_size_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_brain_size, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                  data = brain_size)

# TrkB
  model5.TrkB_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_TrkB, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                            data = TrkB)
# VEGF
  model5.VEGF_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_VEGF, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                            data = VEGF)
# reelin
  model5.reelin_CVR <- rma.mv(yi = CVR, 
                              V = cov_VCVR_reelin, 
                              random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                              mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                              data = reelin)
# GFAP
  model5.GFAP_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_GFAP, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                            data = GFAP)
# syptophysin
  model5.syptophysin_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_syptophysin, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                   data = syptophysin)
# mitochondrial_biogenesis
  model5.mitochondrial_biogenesis_CVR <- rma.mv(yi = CVR, 
                                                V = cov_VCVR_mitochondrial_biogenesis, 
                                                random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                                data = mitochondrial_biogenesis)
# DNA_methylation
  model5.DNA_methylation_CVR <- rma.mv(yi = CVR, 
                                       V = VCVR, 
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                       data = DNA_methylation)
# learning_MWM
  model5.learning_MWM_CVR <- rma.mv(yi = CVR, 
                                    V = cov_VCVR_learning_MWM, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                    data = learning_MWM)
# memory_MWM
  model5.memory_MWM_CVR <- rma.mv(yi = CVR, 
                                  V = VCVR,#cov_VCVR_memory_MWM, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                  data = memory_MWM)
# memory_NOR
  model5.memory_NOR_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_memory_NOR, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                  data = memory_NOR)
# anxiety_OFT
  model5.anxiety_OFT_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_anxiety_OFT, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                   data = anxiety_OFT)
# anxiety_EPM
  model5.anxiety_EPM_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_anxiety_EPM, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(manipulation_window, ref = 'pre-conception') -1, 
                                   data = anxiety_EPM)

#--------------------- grouped traits----------------------#		



# brain_development
  model5.brain_development_CVR <- rma.mv(yi = CVR, 
                                         V = cov_VCVR_brain_development, 
                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                         mod = ~relevel(manipulation_window, ref = 'pre-conception') -1,
                                         data = brain_development)	


# genes
  model5.genes_CVR <- rma.mv(yi = CVR, 
                             V = cov_VCVR_genes, 
                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                             mod = ~relevel(manipulation_window, ref = 'pre-conception') -1,
                             data = genes)


# behavior
  model5.behavior_CVR <- rma.mv(yi = CVR, 
                                V = cov_VCVR_behavior, 
                                random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                mod = ~relevel(manipulation_window, ref = 'pre-conception') -1,
                               data = behavior)	



# Saving models
 # Improvement (lnRR) 
   save(model5.neuron_count_RR, file = './models/model5.neuron_count_RR.Rdata')
   save(model5.brain_size_RR, file = './models/model5.brain_size_RR.Rdata')
   save(model5.BDNF_RR, file = './models/model5.BDNF_RR.Rdata')
   save(model5.TrkB_RR, file = './models/model5.TrkB_RR.Rdata')
   save(model5.VEGF_RR, file = './models/model5.VEGF_RR.Rdata')
   save(model5.reelin_RR, file = './models/model5.reelin_RR.Rdata')
   save(model5.GFAP_RR, file = './models/model5.GFAP_RR.Rdata')
   save(model5.syptophysin_RR, file = './models/model5.syptophysin_RR.Rdata')
   save(model5.mitochondrial_biogenesis_RR, file = './models/model5.mitochondrial_biogenesis_RR.Rdata')
   save(model5.DNA_methylation_RR, file = './models/model5.DNA_methylation_RR.Rdata')
   save(model5.learning_MWM_RR, file = './models/model5.learning_MWM_RR.Rdata')
   save(model5.memory_MWM_RR, file = './models/model5.memory_MWM_RR.Rdata')
   save(model5.memory_NOR_RR, file = './models/model5.memory_NOR_RR.Rdata')
   save(model5.anxiety_OFT_RR, file = './models/model5.anxiety_OFT_RR.Rdata')
   save(model5.anxiety_EPM_RR, file = './models/model5.anxiety_EPM_RR.Rdata')
   save(model5.behavior_RR, file = './models/model5.behavior_RR.Rdata')
   save(model5.brain_development_RR, file = './models/model5.brain_development_RR.Rdata')

 # Inter-individual differences (lnCVR) 
  save(model5.neuron_count_CVR, file = './models/model5.neuron_count_CVR.Rdata')
  save(model5.brain_size_CVR, file = './models/model5.brain_size_CVR.Rdata')
  save(model5.BDNF_CVR, file = './models/model5.BDNF_CVR.Rdata')
  save(model5.TrkB_CVR, file = './models/model5.TrkB_CVR.Rdata')
  save(model5.VEGF_CVR, file = './models/model5.VEGF_CVR.Rdata')
  save(model5.reelin_CVR, file = './models/model5.reelin_CVR.Rdata')
  save(model5.GFAP_CVR, file = './models/model5.GFAP_CVR.Rdata')
  save(model5.syptophysin_CVR, file = './models/model5.syptophysin_CVR.Rdata')
  save(model5.mitochondrial_biogenesis_CVR, file = './models/model5.mitochondrial_biogenesis_CVR.Rdata')
  save(model5.DNA_methylation_CVR, file = './models/model5.DNA_methylation_CVR.Rdata')
  save(model5.learning_MWM_CVR, file = './models/model5.learning_MWM_CVR.Rdata')
  save(model5.memory_MWM_CVR, file = './models/model5.memory_MWM_CVR.Rdata')
  save(model5.memory_NOR_CVR, file = './models/model5.memory_NOR_CVR.Rdata')
  save(model5.anxiety_OFT_CVR, file = './models/model5.anxiety_OFT_CVR.Rdata')
  save(model5.anxiety_EPM_CVR, file = './models/model5.anxiety_EPM_CVR.Rdata')
  save(model5.genes_CVR, file = './models/model5.genes_CVR.Rdata')
  save(model5.brain_development_CVR, file = './models/model5.brain_development_CVR.Rdata')
```




#### (vi) Univariate regression model - F1 ontogenetic stage

```{r F1 ontogenetic stage}
#***************************************************************#
#--------------------- Improvement (lnRR) ----------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model6.neuron_count_RR <- rma.mv(yi = RR, 
                                   V = cov_VRR_neuron_count, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~response_age_life_phase -1, 
                                   data = neuron_count)

# BDNF
model6.BDNF_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_BDNF, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~response_age_life_phase -1, 
                                 data = BDNF)

# brain_size
  model6.brain_size_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_brain_size, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~response_age_life_phase -1, 
                                 data = brain_size)

# TrkB
  model6.TrkB_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_TrkB, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~response_age_life_phase -1, 
                           data = TrkB)
# VEGF
  model6.VEGF_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_VEGF, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~response_age_life_phase -1, 
                          data = VEGF)
# reelin
  model6.reelin_RR <- rma.mv(yi = RR, 
                             V = cov_VRR_reelin, 
                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                             mod = ~response_age_life_phase -1, 
                             data = reelin)
# GFAP
  model6.GFAP_RR <- rma.mv(yi = RR, 
                           V = cov_VRR_GFAP, 
                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                           mod = ~response_age_life_phase -1, 
                           data = GFAP)
# syptophysin
  model6.syptophysin_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_syptophysin, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~response_age_life_phase -1, 
                                  data = syptophysin)
# mitochondrial_biogenesis
  model6.mitochondrial_biogenesis_RR <- rma.mv(yi = RR, 
                                               V = VRR, 
                                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                               mod = ~response_age_life_phase -1, 
                                               data = mitochondrial_biogenesis)
# DNA_methylation
  model6.DNA_methylation_RR <- rma.mv(yi = RR, 
                                      V = VRR, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~response_age_life_phase -1, 
                                      data = DNA_methylation)
# learning_MWM
  model6.learning_MWM_RR <- rma.mv(yi = RR, 
                                   V = cov_VRR_learning_MWM, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~response_age_life_phase -1, 
                                   data = learning_MWM)
# memory_MWM
  model6.memory_MWM_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_memory_MWM, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~response_age_life_phase -1, 
                                 data = memory_MWM)
# memory_NOR
  model6.memory_NOR_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_memory_NOR, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~response_age_life_phase -1, 
                                 data = memory_NOR)
# anxiety_OFT
  model6.anxiety_OFT_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_anxiety_OFT, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~response_age_life_phase -1, 
                                  data = anxiety_OFT)
# anxiety_EPM
  model6.anxiety_EPM_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_anxiety_EPM, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mods = ~response_age_life_phase -1, 
                                  data = anxiety_EPM)

#--------------------- Board traits----------------------#



# genes
  model6.genes_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_genes, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~response_age_life_phase -1,
                                  data = genes)


# behavior
model6.behavior_RR <- rma.mv(yi = RR, 
                             V = cov_VRR_behavior, 
                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                             mod = ~response_age_life_phase -1,
                             data = behavior)

# brain_development
  model6.brain_development_RR <- rma.mv(yi = RR, 
                                        V = cov_VRR_brain_development, 
                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                        mod = ~response_age_life_phase -1,
                                        data = brain_development)


#***************************************************************#
#------------------ Inter-individual differences (lnCVR) -------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model6.neuron_count_CVR <- rma.mv(yi = CVR, 
                                    V = cov_VCVR_neuron_count, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~response_age_life_phase -1, 
                                    data = neuron_count)

# BDNF
  model6.BDNF_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_BDNF, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~response_age_life_phase -1, 
                            data = BDNF)
# brain_size
  model6.brain_size_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_brain_size, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~response_age_life_phase -1, 
                                  data = brain_size)
# TrkB
  model6.TrkB_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_TrkB, 
                            random = list(~1|study_ID, ~1|ES_ID),
                            mod = ~response_age_life_phase -1, 
                            data = TrkB)
# VEGF
  model6.VEGF_CVR <- rma.mv(yi = CVR, 
                            V = cov_VCVR_VEGF, 
                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                            mod = ~response_age_life_phase -1, 
                            data = VEGF)
# reelin
  model6.reelin_CVR <- rma.mv(yi = CVR, 
                              V = cov_VCVR_reelin, 
                              random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                              mod = ~response_age_life_phase -1, 
                              data = reelin)
# GFAP
  model6.GFAP_CVR <- rma.mv(yi = CVR, 
                            V = VCVR,#cov_VCVR_GFAP, 
                            random = list(~1|study_ID, ~1|ES_ID),
                            mod = ~response_age_life_phase -1, 
                            data = GFAP)
# syptophysin
  model6.syptophysin_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_syptophysin, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~response_age_life_phase -1, 
                                   data = syptophysin)
# mitochondrial_biogenesis
  model6.mitochondrial_biogenesis_CVR <- rma.mv(yi = CVR, 
                                                V = cov_VCVR_mitochondrial_biogenesis, 
                                                random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                mod = ~response_age_life_phase -1, 
                                                data = mitochondrial_biogenesis)
# DNA_methylation
  model6.DNA_methylation_CVR <- rma.mv(yi = CVR, 
                                       V = VCVR, 
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       mod = ~response_age_life_phase -1, 
                                       data = DNA_methylation)
# learning_MWM
  model6.learning_MWM_CVR <- rma.mv(yi = CVR, 
                                    V = cov_VCVR_learning_MWM, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~response_age_life_phase -1, 
                                    data = learning_MWM)
# memory_MWM
  model6.memory_MWM_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_memory_MWM, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~response_age_life_phase -1, 
                                  data = memory_MWM)
# memory_NOR
  model6.memory_NOR_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_memory_NOR, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~response_age_life_phase -1, 
                                  data = memory_NOR)
# anxiety_OFT
  model6.anxiety_OFT_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_anxiety_OFT, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~response_age_life_phase -1, 
                                   data = anxiety_OFT)
# anxiety_EPM
  model6.anxiety_EPM_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_anxiety_EPM, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~response_age_life_phase -1, 
                                   data = anxiety_EPM)

#--------------------- Board traits----------------------#		


# genes
  model6.genes_CVR <- rma.mv(yi = CVR, 
                             V = cov_VCVR_genes, 
                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                             mod = ~response_age_life_phase -1,
                             data = genes)


# behavior
model6.behavior_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_behavior, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~response_age_life_phase -1,
                                  data = behavior)

# brain_development
  model6.brain_development_CVR <- rma.mv(yi = CVR, 
                                         V = cov_VCVR_brain_development, 
                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                         mod = ~response_age_life_phase -1,
                                         data = brain_development)


# Saving models
 # Improvement (lnRR) 
   save(model6.neuron_count_RR, file = './models/model6.neuron_count_RR.Rdata')
   save(model6.brain_size_RR, file = './models/model6.brain_size_RR.Rdata')
   save(model6.BDNF_RR, file = './models/model6.BDNF_RR.Rdata')
   save(model6.TrkB_RR, file = './models/model6.TrkB_RR.Rdata')
   save(model6.VEGF_RR, file = './models/model6.VEGF_RR.Rdata')
   save(model6.reelin_RR, file = './models/model6.reelin_RR.Rdata')
   save(model6.GFAP_RR, file = './models/model6.GFAP_RR.Rdata')
   save(model6.syptophysin_RR, file = './models/model6.syptophysin_RR.Rdata')
   save(model6.mitochondrial_biogenesis_RR, file = './models/model6.mitochondrial_biogenesis_RR.Rdata')
   save(model6.DNA_methylation_RR, file = './models/model6.DNA_methylation_RR.Rdata')
   save(model6.learning_MWM_RR, file = './models/model6.learning_MWM_RR.Rdata')
   save(model6.memory_MWM_RR, file = './models/model6.memory_MWM_RR.Rdata')
   save(model6.memory_NOR_RR, file = './models/model6.memory_NOR_RR.Rdata')
   save(model6.anxiety_OFT_RR, file = './models/model6.anxiety_OFT_RR.Rdata')
   save(model6.anxiety_EPM_RR, file = './models/model6.anxiety_EPM_RR.Rdata')
   save(model6.genes_RR, file = './models/model6.genes_RR.Rdata')
   save(model6.behavior_RR, file = './models/model6.behavior_RR.Rdata')
   save(model6.brain_development_RR, file = './models/model6.brain_development_RR.Rdata')

 # Inter-individual differences (lnCVR) 
   save(model6.neuron_count_CVR, file = './models/model6.neuron_count_CVR.Rdata')
   save(model6.brain_size_CVR, file = './models/model6.brain_size_CVR.Rdata')
   save(model6.BDNF_CVR, file = './models/model6.BDNF_CVR.Rdata')
   save(model6.TrkB_CVR, file = './models/model6.TrkB_CVR.Rdata')
   save(model6.VEGF_CVR, file = './models/model6.VEGF_CVR.Rdata')
   save(model6.reelin_CVR, file = './models/model6.reelin_CVR.Rdata')
   save(model6.GFAP_CVR, file = './models/model6.GFAP_CVR.Rdata')
   save(model6.syptophysin_CVR, file = './models/model6.syptophysin_CVR.Rdata')
   save(model6.mitochondrial_biogenesis_CVR, file = './models/model6.mitochondrial_biogenesis_CVR.Rdata')
   save(model6.DNA_methylation_CVR, file = './models/model6.DNA_methylation_CVR.Rdata')
   save(model6.learning_MWM_CVR, file = './models/model6.learning_MWM_CVR.Rdata')
   save(model6.memory_MWM_CVR, file = './models/model6.memory_MWM_CVR.Rdata')
   save(model6.memory_NOR_CVR, file = './models/model6.memory_NOR_CVR.Rdata')
   save(model6.anxiety_OFT_CVR, file = './models/model6.anxiety_OFT_CVR.Rdata')
   save(model6.anxiety_EPM_CVR, file = './models/model6.anxiety_EPM_CVR.Rdata')
   save(model6.genes_CVR, file = './models/model6.genes_CVR.Rdata')
   save(model6.behavior_CVR, file = './models/model6.behavior_CVR.Rdata')
   save(model6.brain_development_CVR, file = './models/model6.brain_development_CVR.Rdata')
```






### 3. Contrast models


#### (ii) Univariate regression model - parental sex

```{r parental sex}
#***************************************************************#
#--------------------- Improvement (lnRR) ----------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model.contrast2.neuron_count_RR <- rma.mv(yi = RR, 
                                            V = cov_VRR_neuron_count, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                            data = neuron_count)

# BDNF
  model.contrast2.BDNF_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_BDNF, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                  data = BDNF)

# brain_siz
model.contrast2.brain_size_RR <- rma.mv(yi = RR, 
                                        V = cov_VRR_brain_size, 
                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                        mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                        data = brain_size)

# TrkB
  model.contrast2.TrkB_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_TrkB, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                    data = TrkB)

# VEGF
  model.contrast2.VEGF_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_VEGF, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                    data = VEGF)
# reelin
  model.contrast2.reelin_RR <- rma.mv(yi = RR, 
                                      V = cov_VRR_reelin, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                      data = reelin)
# GFAP
  model.contrast2.GFAP_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_GFAP, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                    data = GFAP)
# syptophysin
  model.contrast2.syptophysin_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_syptophysin, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                           data = syptophysin)
# mitochondrial_biogenesis
  model.contrast2.mitochondrial_biogenesis_RR <- rma.mv(yi = RR, 
                                                        V = cov_VRR_mitochondrial_biogenesis, 
                                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                        mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                                        data = mitochondrial_biogenesis)
# DNA_methylation
  model.contrast2.DNA_methylation_RR <- rma.mv(yi = RR, 
                                               V = VRR, 
                                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                               mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                               data = DNA_methylation)
# learning_MWM
  model.contrast2.learning_MWM_RR <- rma.mv(yi = RR, 
                                            V = cov_VRR_learning_MWM, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                            data = learning_MWM)
# memory_MWM
  model.contrast2.memory_MWM_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_memory_MWM, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                          data = memory_MWM)
# memory_NOR
  model.contrast2.memory_NOR_RR <- rma.mv(yi = RR, 
                                          V = VRR,#cov_VRR_memory_NOR, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                          data = memory_NOR)
# anxiety_OFT
  model.contrast2.anxiety_OFT_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_anxiety_OFT, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                           data = anxiety_OFT)
# anxiety_EPM
  model.contrast2.anxiety_EPM_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_anxiety_EPM, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                           data = anxiety_EPM)

#--------------------- Board traits----------------------#

# brain_development
  model.contrast2.brain_development_RR <- rma.mv(yi = RR, 
                                                 V = cov_VRR_brain_development, 
                                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                 mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                                 data = brain_development)

# genes
  model.contrast2.genes_RR <- rma.mv(yi = RR, 
                                     V = cov_VRR_genes, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                     data = genes)


# behavior
  model.contrast2.behavior_RR <- rma.mv(yi = RR, 
                                        V = cov_VRR_behavior, 
                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                        mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                        data = behavior)


#***************************************************************#
#------------------ Inter-individual differences (lnCVR) -------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model.contrast2.neuron_count_CVR <- rma.mv(yi = CVR, 
                                             V = cov_VCVR_neuron_count, 
                                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                             mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                             data = neuron_count)

# brain_size
  model.contrast2.brain_size_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_brain_size, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                           data = brain_size)

# BDNF
  model.contrast2.BDNF_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_BDNF, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                     data = BDNF)

#TrkB
  model.contrast2.TrkB_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_TrkB, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                     data = TrkB)
# VEGF
  model.contrast2.VEGF_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_VEGF, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                     data = VEGF)
# reelin
  model.contrast2.reelin_CVR <- rma.mv(yi = CVR, 
                                       V = cov_VCVR_reelin, 
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                       data = reelin)
# GFAP
  model.contrast2.GFAP_CVR <- rma.mv(yi = CVR, 
                                     V = VCVR,
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                     data = GFAP)
# syptophysin
  model.contrast2.syptophysin_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_syptophysin, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                            data = syptophysin)
# mitochondrial_biogenesis
  model.contrast2.mitochondrial_biogenesis_CVR <- rma.mv(yi = CVR, 
                                                         V = cov_VCVR_mitochondrial_biogenesis, 
                                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                         mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                                         data = mitochondrial_biogenesis)
# DNA_methylation
  model.contrast2.DNA_methylation_CVR <- rma.mv(yi = CVR, 
                                                V = VCVR, 
                                                random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                                data = DNA_methylation)
# learning_MWM
  model.contrast2.learning_MWM_CVR <- rma.mv(yi = CVR, 
                                             V = cov_VCVR_learning_MWM, 
                                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                             mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                             data = learning_MWM)
# memory_MWM
  model.contrast2.memory_MWM_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_memory_MWM, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                           data = memory_MWM)
# memory_NOR
  model.contrast2.memory_NOR_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_memory_NOR, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                           data = memory_NOR)
# anxiety_OFT
  model.contrast2.anxiety_OFT_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_anxiety_OFT, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                            data = anxiety_OFT)
# anxiety_EPM
  model.contrast2.anxiety_EPM_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_anxiety_EPM, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                            data = anxiety_EPM)

#--------------------- Board traits----------------------#		

# brain_development
  model.contrast2.brain_development_CVR <- rma.mv(yi = CVR, 
                                                  V = cov_VCVR_brain_development, 
                                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                  mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                                  data = brain_development)


# genes
  model.contrast2.genes_CVR <- rma.mv(yi = CVR, 
                                      V = cov_VCVR_genes, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                      data = genes)


# behavior
  model.contrast2.behavior_CVR <- rma.mv(yi = CVR, 
                                         V = cov_VCVR_behavior, 
                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                         mod = ~relevel(F0_sex_exercise, ref = 'male'), 
                                         data = behavior)


# Saving models

 # Improvement (lnRR) 
   save(model.contrast2.neuron_count_RR, file = './models/model.contrast2.neuron_count_RR.Rdata')
   save(model.contrast2.brain_size_RR, file = './models/model.contrast2.brain_size_RR.Rdata')
   save(model.contrast2.BDNF_RR, file = './models/model.contrast2.BDNF_RR.Rdata')
   save(model.contrast2.TrkB_RR, file = './models/model.contrast2.TrkB_RR.Rdata')
   save(model.contrast2.VEGF_RR, file = './models/model.contrast2.VEGF_RR.Rdata')
   save(model.contrast2.reelin_RR, file = './models/model.contrast2.reelin_RR.Rdata')
   save(model.contrast2.GFAP_RR, file = './models/model.contrast2.GFAP_RR.Rdata')
   save(model.contrast2.syptophysin_RR, file = './models/model.contrast2.syptophysin_RR.Rdata')
  save(model.contrast2.mitochondrial_biogenesis_RR, file = './models/model.contrast2.mitochondrial_biogenesis_RR.Rdata')
  save(model.contrast2.DNA_methylation_RR, file = './models/model.contrast2.DNA_methylation_RR.Rdata')
  save(model.contrast2.learning_MWM_RR, file = './models/model.contrast2.learning_MWM_RR.Rdata')
  save(model.contrast2.memory_MWM_RR, file = './models/model.contrast2.memory_MWM_RR.Rdata')
  save(model.contrast2.memory_NOR_RR, file = './models/model.contrast2.memory_NOR_RR.Rdata')
  save(model.contrast2.anxiety_OFT_RR, file = './models/model.contrast2.anxiety_OFT_RR.Rdata')
  save(model.contrast2.anxiety_EPM_RR, file = './models/model.contrast2.anxiety_EPM_RR.Rdata')
  save(model.contrast2.genes_RR, file = './models/model.contrast2.genes_RR.Rdata')
  save(model.contrast2.behavior_RR, file = './models/model.contrast2.behavior_RR.Rdata')
  save(model.contrast2.brain_development_RR, file = './models/model.contrast2.brain_development_RR.Rdata')

 # Inter-individual differences (lnCVR) 
   save(model.contrast2.neuron_count_CVR, file = './models/model.contrast2.neuron_count_CVR.Rdata')
   save(model.contrast2.brain_size_CVR, file = './models/model.contrast2.brain_size_CVR.Rdata')
   save(model.contrast2.BDNF_CVR, file = './models/model.contrast2.BDNF_CVR.Rdata')
   save(model.contrast2.TrkB_CVR, file = './models/model.contrast2.TrkB_CVR.Rdata')
   save(model.contrast2.VEGF_CVR, file = './models/model.contrast2.VEGF_CVR.Rdata')
   save(model.contrast2.reelin_CVR, file = './models/model.contrast2.reelin_CVR.Rdata')
   save(model.contrast2.GFAP_CVR, file = './models/model.contrast2.GFAP_CVR.Rdata')
   save(model.contrast2.syptophysin_CVR, file = './models/model.contrast2.syptophysin_CVR.Rdata')
   save(model.contrast2.mitochondrial_biogenesis_CVR, file = './models/model.contrast2.mitochondrial_biogenesis_CVR.Rdata')
   save(model.contrast2.DNA_methylation_CVR, file = './models/model.contrast2.DNA_methylation_CVR.Rdata')
   save(model.contrast2.learning_MWM_CVR, file = './models/model.contrast2.learning_MWM_CVR.Rdata')
   save(model.contrast2.memory_MWM_CVR, file = './models/model.contrast2.memory_MWM_CVR.Rdata')
   save(model.contrast2.memory_NOR_CVR, file = './models/model.contrast2.memory_NOR_CVR.Rdata')
   save(model.contrast2.anxiety_OFT_CVR, file = './models/model.contrast2.anxiety_OFT_CVR.Rdata')
   save(model.contrast2.anxiety_EPM_CVR, file = './models/model.contrast2.anxiety_EPM_CVR.Rdata')
   save(model.contrast2.genes_CVR, file = './models/model.contrast2.genes_CVR.Rdata')
   save(model.contrast2.behavior_CVR, file = './models/model.contrast2.behavior_CVR.Rdata')
   save(model.contrast2.brain_development_CVR, file = './models/model.contrast2.brain_development_CVR.Rdata')
```


#### (iii) Univariate regression model - offspring sex

```{r offspring sex}
#***************************************************************#
#--------------------- Improvement (lnRR) ----------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model.contrast3.neuron_count_RR <- rma.mv(yi = RR, 
                                            V = cov_VRR_neuron_count, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(F1_sex_test, ref = 'male'), 
                                            data = neuron_count)

# brain_size
  model.contrast3.brain_size_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_brain_size, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~relevel(F1_sex_test, ref = 'male'), 
                                          data = brain_size)

# BDNF
  model.contrast3.BDNF_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_BDNF, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(F1_sex_test, ref = 'male'), 
                                    data = BDNF)

# TrkB
  model.contrast3.TrkB_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_TrkB, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(F1_sex_test, ref = 'male'),  # no  female F1
                                    data = TrkB)
# VEGF
  model.contrast3.VEGF_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_VEGF, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(F1_sex_test, ref = 'male'), 
                                    data = VEGF)
# reelin
  model.contrast3.reelin_RR <- rma.mv(yi = RR, 
                                      V = cov_VRR_reelin, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~relevel(F1_sex_test, ref = 'male'), 
                                      data = reelin)

# GFAP
  model.contrast3.GFAP_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_GFAP, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(F1_sex_test, ref = 'male'), # no  female F1
                                    data = GFAP)
# syptophysin
  model.contrast3.syptophysin_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_syptophysin, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(F1_sex_test, ref = 'male'), # no  female F1
                                           data = syptophysin)
# mitochondrial_biogenesis
  model.contrast3.mitochondrial_biogenesis_RR <- rma.mv(yi = RR, 
                                                        V = cov_VRR_mitochondrial_biogenesis, 
                                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                        mod = ~relevel(F1_sex_test, ref = 'male'), # no  female F1
                                                        data = mitochondrial_biogenesis)
# DNA_methylation
  model.contrast3.DNA_methylation_RR <- rma.mv(yi = RR, 
                                               V = VRR, 
                                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                               mod = ~relevel(F1_sex_test, ref = 'male'), # no  female F1
                                               data = DNA_methylation)
# learning_MWM
  model.contrast3.learning_MWM_RR <- rma.mv(yi = RR, 
                                            V = cov_VRR_learning_MWM, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(F1_sex_test, ref = 'male'), 
                                            data = learning_MWM)
# memory_MWM
  model.contrast3.memory_MWM_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_memory_MWM, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~relevel(F1_sex_test, ref = 'male'), 
                                          data = memory_MWM)
# memory_NOR
  model.contrast3.memory_NOR_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_memory_NOR, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~relevel(F1_sex_test, ref = 'male'), 
                                          data = memory_NOR)
# anxiety_OFT
  model.contrast3.anxiety_OFT_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_anxiety_OFT, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(F1_sex_test, ref = 'male'), 
                                           data = anxiety_OFT)
# anxiety_EPM
  model.contrast3.anxiety_EPM_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_anxiety_EPM, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(F1_sex_test, ref = 'male'), 
                                           data = anxiety_EPM)

#--------------------- Board traits----------------------#


# brain_development
  model.contrast3.brain_development_RR <- rma.mv(yi = RR, 
                                                 V = cov_VRR_brain_development, 
                                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                 mod = ~relevel(F1_sex_test, ref = 'male'), 
                                                 data = brain_development)

# genes
  model.contrast3.genes_RR <- rma.mv(yi = RR, 
                                     V = cov_VRR_genes, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(F1_sex_test, ref = 'male'), 
                                     data = genes)

# behavior
  model.contrast3.behavior_RR <- rma.mv(yi = RR, 
                                        V = cov_VRR_behavior, 
                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                        mod = ~relevel(F1_sex_test, ref = 'male'), 
                                        data = behavior)

#***************************************************************#
#------------------ Inter-individual differences (lnCVR) -------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model.contrast3.neuron_count_CVR <- rma.mv(yi = CVR, 
                                             V = cov_VCVR_neuron_count, 
                                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                             mod = ~relevel(F1_sex_test, ref = 'male'), 
                                             data = neuron_count)

# brain_size
  model.contrast3.brain_size_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_brain_size, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(F1_sex_test, ref = 'male'), 
                                           data = brain_size)

# BDNF
  model.contrast3.BDNF_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_BDNF, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(F1_sex_test, ref = 'male'), 
                                     data = BDNF)

# TrkB
  model.contrast3.TrkB_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_TrkB, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(F1_sex_test, ref = 'male'), 
                                     data = TrkB)
# VEGF
  model.contrast3.VEGF_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_VEGF, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(F1_sex_test, ref = 'male'), 
                                     data = VEGF)
# reelin
  model.contrast3.reelin_CVR <- rma.mv(yi = CVR, 
                                       V = cov_VCVR_reelin, 
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       mod = ~relevel(F1_sex_test, ref = 'male'), 
                                       data = reelin)
# GFAP
  model.contrast3.GFAP_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_GFAP, 
                                     random = list(~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(F1_sex_test, ref = 'male'), 
                                     data = GFAP)
# syptophysin
  model.contrast3.syptophysin_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_syptophysin, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(F1_sex_test, ref = 'male'), 
                                     data = syptophysin)
# mitochondrial_biogenesis
  model.contrast3.mitochondrial_biogenesis_CVR <- rma.mv(yi = CVR, 
                                    V = cov_VCVR_mitochondrial_biogenesis, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(F1_sex_test, ref = 'male'), 
                                    data = mitochondrial_biogenesis)
# DNA_methylation
  model.contrast3.DNA_methylation_CVR <- rma.mv(yi = CVR, 
                                                V = VCVR, 
                                                random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                mod = ~relevel(F1_sex_test, ref = 'male'), 
                                                data = DNA_methylation)
# learning_MWM
  model.contrast3.learning_MWM_CVR <- rma.mv(yi = CVR, 
                                             V = cov_VCVR_learning_MWM, 
                                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                             mod = ~relevel(F1_sex_test, ref = 'male'), 
                                             data = learning_MWM)
# memory_MWM
  model.contrast3.memory_MWM_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_memory_MWM, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(F1_sex_test, ref = 'male'), 
                                           data = memory_MWM)
# memory_NOR
  model.contrast3.memory_NOR_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_memory_NOR, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(F1_sex_test, ref = 'male'), 
                                           data = memory_NOR)
# anxiety_OFT
  model.contrast3.anxiety_OFT_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_anxiety_OFT, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(F1_sex_test, ref = 'male'), 
                                            data = anxiety_OFT)
# anxiety_EPM
  model.contrast3.anxiety_EPM_CVR <- rma.mv(yi = CVR, 
                                          V = cov_VCVR_anxiety_EPM, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~relevel(F1_sex_test, ref = 'male'), 
                                          data = anxiety_EPM)

#--------------------- grouped traits----------------------#		


# brain_development
  model.contrast3.brain_development_CVR <- rma.mv(yi = CVR, 
                                                  V = cov_VCVR_brain_development, 
                                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                  mod = ~relevel(F1_sex_test, ref = 'male'),
                                                  data = brain_development)	

# genes
model.contrast3.genes_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_genes, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(F1_sex_test, ref = 'male'), 
                                  data = genes)

# behavior
  model.contrast3.behavior_CVR <- rma.mv(yi = CVR, 
                                         V = cov_VCVR_behavior, 
                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                         mod = ~relevel(F1_sex_test, ref = 'male'),
                                         data = behavior)	


# Saving models
 # Improvement (lnRR) 
   save(model.contrast3.neuron_count_RR, file = './models/model.contrast3.neuron_count_RR.Rdata')
   save(model.contrast3.brain_size_RR, file = './models/model.contrast3.brain_size_RR.Rdata')
   save(model.contrast3.BDNF_RR, file = './models/model.contrast3.BDNF_RR.Rdata')
   save(model.contrast3.TrkB_RR, file = './models/model.contrast3.TrkB_RR.Rdata')
   save(model.contrast3.VEGF_RR, file = './models/model.contrast3.VEGF_RR.Rdata')
   save(model.contrast3.reelin_RR, file = './models/model.contrast3.reelin_RR.Rdata')
   save(model.contrast3.GFAP_RR, file = './models/model.contrast3.GFAP_RR.Rdata')
   save(model.contrast3.syptophysin_RR, file = './models/model.contrast3.syptophysin_RR.Rdata')
   save(model.contrast3.mitochondrial_biogenesis_RR, file = './models/model.contrast3.mitochondrial_biogenesis_RR.Rdata')
   save(model.contrast3.DNA_methylation_RR, file = './models/model.contrast3.DNA_methylation_RR.Rdata')
   save(model.contrast3.learning_MWM_RR, file = './models/model.contrast3.learning_MWM_RR.Rdata')
   save(model.contrast3.memory_MWM_RR, file = './models/model.contrast3.memory_MWM_RR.Rdata')
   save(model.contrast3.memory_NOR_RR, file = './models/model.contrast3.memory_NOR_RR.Rdata')
   save(model.contrast3.anxiety_OFT_RR, file = './models/model.contrast3.anxiety_OFT_RR.Rdata')
   save(model.contrast3.anxiety_EPM_RR, file = './models/model.contrast3.anxiety_EPM_RR.Rdata')
   save(model.contrast3.genes_RR, file = './models/model.contrast3.genes_RR.Rdata')
   save(model.contrast3.behavior_RR, file = './models/model.contrast3.behavior_RR.Rdata')
   save(model.contrast3.brain_development_RR, file = './models/model.contrast3.brain_development_RR.Rdata')

 # Inter-individual differences (lnCVR) 
   save(model.contrast3.neuron_count_CVR, file = './models/model.contrast3.neuron_count_CVR.Rdata')
   save(model.contrast3.brain_size_CVR, file = './models/model.contrast3.brain_size_CVR.Rdata')
   save(model.contrast3.BDNF_CVR, file = './models/model.contrast3.BDNF_CVR.Rdata')
   save(model.contrast3.TrkB_CVR, file = './models/model.contrast3.TrkB_CVR.Rdata')
   save(model.contrast3.VEGF_CVR, file = './models/model.contrast3.VEGF_CVR.Rdata')
   save(model.contrast3.reelin_CVR, file = './models/model.contrast3.reelin_CVR.Rdata')
   save(model.contrast3.GFAP_CVR, file = './models/model.contrast3.GFAP_CVR.Rdata')
   save(model.contrast3.syptophysin_CVR, file = './models/model.contrast3.syptophysin_CVR.Rdata')
   save(model.contrast3.mitochondrial_biogenesis_CVR, file = './models/model.contrast3.mitochondrial_biogenesis_CVR.Rdata')
   save(model.contrast3.DNA_methylation_CVR, file = './models/model.contrast3.DNA_methylation_CVR.Rdata')
   save(model.contrast3.learning_MWM_CVR, file = './models/model.contrast3.learning_MWM_CVR.Rdata')
   save(model.contrast3.memory_MWM_CVR, file = './models/model.contrast3.memory_MWM_CVR.Rdata')
   save(model.contrast3.memory_NOR_CVR, file = './models/model.contrast3.memory_NOR_CVR.Rdata')
   save(model.contrast3.anxiety_OFT_CVR, file = './models/model.contrast3.anxiety_OFT_CVR.Rdata')
   save(model.contrast3.anxiety_EPM_CVR, file = './models/model.contrast3.anxiety_EPM_CVR.Rdata')
   save(model.contrast3.genes_CVR, file = './models/model.contrast3.genes_CVR.Rdata')
   save(model.contrast3.behavior_CVR, file = './models/model.contrast3.behavior_CVR.Rdata')
   save(model.contrast3.brain_development_CVR, file = './models/model.contrast3.brain_development_CVR.Rdata')
```



#### (iv) Univariate regression mode - exerise mode

```{r exercise mode}
#***************************************************************#
#--------------------- Improvement (lnRR) ----------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model.contrast4.neuron_count_RR <- rma.mv(yi = RR, 
                                            V = cov_VRR_neuron_count, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                            data = neuron_count)

# brain_size
  model.contrast4.brain_size_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_brain_size, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                          data = brain_size)


# BDNF
  model.contrast4.BDNF_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_BDNF, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                    data = BDNF)


# TrkB
  model.contrast4.TrkB_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_TrkB, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                    data = TrkB)
# VEGF
model.contrast4.VEGF_RR <- rma.mv(yi = RR, 
                                 V = cov_VRR_VEGF, 
                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                 mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                 data = VEGF)
# reelin
  model.contrast4.reelin_RR <- rma.mv(yi = RR, 
                                      V = cov_VRR_reelin, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                      data = reelin)
# GFAP
  model.contrast4.GFAP_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_GFAP, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                    data = GFAP)
# syptophysin
  model.contrast4.syptophysin_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_syptophysin, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                           data = syptophysin)
# mitochondrial_biogenesis
  model.contrast4.mitochondrial_biogenesis_RR <- rma.mv(yi = RR, 
                                                        V = cov_VRR_mitochondrial_biogenesis, 
                                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                        mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                                        data = mitochondrial_biogenesis)
# DNA_methylation
  model.contrast4.DNA_methylation_RR <- rma.mv(yi = RR, 
                                               V = VRR, 
                                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                               mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                               data = DNA_methylation)
# learning_MWM
  model.contrast4.learning_MWM_RR <- rma.mv(yi = RR, 
                                            V = cov_VRR_learning_MWM, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                            data = learning_MWM)
# memory_MWM
  model.contrast4.memory_MWM_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_memory_MWM, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                          data = memory_MWM)
# memory_NOR
  model.contrast4.memory_NOR_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_memory_NOR, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                          data = memory_NOR)
# anxiety_OFT
  model.contrast4.anxiety_OFT_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_anxiety_OFT, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                           data = anxiety_OFT)
# anxiety_EPM
  model.contrast4.anxiety_EPM_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_anxiety_EPM, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                           data = anxiety_EPM)

#--------------------- Board traits----------------------#

# brain_development
  model.contrast4.brain_development_RR <- rma.mv(yi = RR, 
                                                 V = cov_VRR_brain_development, 
                                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                 mod = ~relevel(manipulation_mode, ref = 'forced'),
                                                 data = brain_development)

# genes
  model.contrast4.genes_RR <- rma.mv(yi = RR, 
                                     V = cov_VRR_genes, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(manipulation_mode, ref = 'forced'),
                                     data = genes)

# behavior
model.contrast4.behavior_RR <- rma.mv(yi = RR, 
                                  V = cov_VRR_behavior, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                  mod = ~relevel(manipulation_mode, ref = 'forced'),
                                  data = behavior)


#***************************************************************#
#------------------ Inter-individual differences (lnCVR) -------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model.contrast4.neuron_count_CVR <- rma.mv(yi = CVR, 
                                             V = cov_VCVR_neuron_count, 
                                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                             mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                             data = neuron_count)

# brain_size
  model.contrast4.brain_size_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_brain_size, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                           data = brain_size)

# BDNF
  model.contrast4.BDNF_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_BDNF, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                     data = BDNF)

# TrkB
  model.contrast4.TrkB_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_TrkB, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                     data = TrkB)
# VEGF
  model.contrast4.VEGF_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_VEGF, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                     data = VEGF)
# reelin
  model.contrast4.reelin_CVR <- rma.mv(yi = CVR, 
                                       V = cov_VCVR_reelin, 
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                       data = reelin)
# GFAP
  model.contrast4.GFAP_CVR <- rma.mv(yi = CVR, 
                                     V = VCVR,#cov_VCVR_GFAP, 
                                     random = list(~1|ES_ID),
                                     mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                     data = GFAP)
# syptophysin
  model.contrast4.syptophysin_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_syptophysin, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                            data = syptophysin)
# mitochondrial_biogenesis
  model.contrast4.mitochondrial_biogenesis_CVR <- rma.mv(yi = CVR, 
                                                         V = VCVR,#cov_VCVR_mitochondrial_biogenesis, 
                                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                         mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                                         data = mitochondrial_biogenesis)
# DNA_methylation
  model.contrast4.DNA_methylation_CVR <- rma.mv(yi = CVR, 
                                                V = VCVR, 
                                                random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                                data = DNA_methylation)
# learning_MWM
  model.contrast4.learning_MWM_CVR <- rma.mv(yi = CVR, 
                                             V = cov_VCVR_learning_MWM, 
                                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                             mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                             data = learning_MWM)
# memory_MWM
  model.contrast4.memory_MWM_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_memory_MWM, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                           data = memory_MWM)
# memory_NOR
  model.contrast4.memory_NOR_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_memory_NOR, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                           data = memory_NOR)
# anxiety_OFT
  model.contrast4.anxiety_OFT_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_anxiety_OFT, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                            data = anxiety_OFT)
# anxiety_EPM
  model.contrast4.anxiety_EPM_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_anxiety_EPM, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(manipulation_mode, ref = 'forced'), 
                                            data = anxiety_EPM)

#--------------------- Board traits----------------------#		


# brain_development
  model.contrast4.brain_development_CVR <- rma.mv(yi = CVR, 
                                                  V = cov_VCVR_brain_development, 
                                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                  mod = ~relevel(manipulation_mode, ref = 'forced'),
                                                  data = brain_development)

# genes
  model.contrast4.genes_CVR <- rma.mv(yi = CVR, 
                                      V = cov_VCVR_genes, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~relevel(manipulation_mode, ref = 'forced'),
                                      data = genes)

# behavior
  model.contrast4.behavior_CVR <- rma.mv(yi = CVR, 
                                         V = VCVR,#cov_VCVR_behavior, 
                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                         mod = ~relevel(manipulation_mode, ref = 'forced'),
                                         data = behavior)



# Saving models
 # Improvement (lnRR) 
   save(model.contrast4.neuron_count_RR, file = './models/model.contrast4.neuron_count_RR.Rdata')
   save(model.contrast4.brain_size_RR, file = './models/model.contrast4.brain_size_RR.Rdata')
   save(model.contrast4.BDNF_RR, file = './models/model.contrast4.BDNF_RR.Rdata')
   save(model.contrast4.TrkB_RR, file = './models/model.contrast4.TrkB_RR.Rdata')
   save(model.contrast4.VEGF_RR, file = './models/model.contrast4.VEGF_RR.Rdata')
   save(model.contrast4.reelin_RR, file = './models/model.contrast4.reelin_RR.Rdata')
   save(model.contrast4.GFAP_RR, file = './models/model.contrast4.GFAP_RR.Rdata')
   save(model.contrast4.syptophysin_RR, file = './models/model.contrast4.syptophysin_RR.Rdata')
   save(model.contrast4.mitochondrial_biogenesis_RR, file = './models/model.contrast4.mitochondrial_biogenesis_RR.Rdata')
   save(model.contrast4.DNA_methylation_RR, file = './models/model.contrast4.DNA_methylation_RR.Rdata')
   save(model.contrast4.learning_MWM_RR, file = './models/model.contrast4.learning_MWM_RR.Rdata')
   save(model.contrast4.memory_MWM_RR, file = './models/model.contrast4.memory_MWM_RR.Rdata')
   save(model.contrast4.memory_NOR_RR, file = './models/model.contrast4.memory_NOR_RR.Rdata')
   save(model.contrast4.anxiety_OFT_RR, file = './models/model.contrast4.anxiety_OFT_RR.Rdata')
   save(model.contrast4.anxiety_EPM_RR, file = './models/model.contrast4.anxiety_EPM_RR.Rdata')
   save(model.contrast4.genes_RR, file = './models/model.contrast4.genes_RR.Rdata')
   save(model.contrast4.behavior_RR, file = './models/model.contrast4.behavior_RR.Rdata')
   save(model.contrast4.brain_development_RR, file = './models/model.contrast4.brain_development_RR.Rdata')

 # Inter-individual differences (lnCVR) 
   save(model.contrast4.neuron_count_CVR, file = './models/model.contrast4.neuron_count_CVR.Rdata')
   save(model.contrast4.brain_size_CVR, file = './models/model.contrast4.brain_size_CVR.Rdata')
   save(model.contrast4.BDNF_CVR, file = './models/model.contrast4.BDNF_CVR.Rdata')
   save(model.contrast4.TrkB_CVR, file = './models/model.contrast4.TrkB_CVR.Rdata')
   save(model.contrast4.VEGF_CVR, file = './models/model.contrast4.VEGF_CVR.Rdata')
   save(model.contrast4.reelin_CVR, file = './models/model.contrast4.reelin_CVR.Rdata')
   save(model.contrast4.GFAP_CVR, file = './models/model.contrast4.GFAP_CVR.Rdata')
   save(model.contrast4.syptophysin_CVR, file = './models/model.contrast4.syptophysin_CVR.Rdata')
   save(model.contrast4.mitochondrial_biogenesis_CVR, file = './models/model.contrast4.mitochondrial_biogenesis_CVR.Rdata')
   save(model.contrast4.DNA_methylation_CVR, file = './models/model.contrast4.DNA_methylation_CVR.Rdata')
   save(model.contrast4.learning_MWM_CVR, file = './models/model.contrast4.learning_MWM_CVR.Rdata')
   save(model.contrast4.memory_MWM_CVR, file = './models/model.contrast4.memory_MWM_CVR.Rdata')
   save(model.contrast4.memory_NOR_CVR, file = './models/model.contrast4.memory_NOR_CVR.Rdata')
   save(model.contrast4.anxiety_OFT_CVR, file = './models/model.contrast4.anxiety_OFT_CVR.Rdata')
   save(model.contrast4.anxiety_EPM_CVR, file = './models/model.contrast4.anxiety_EPM_CVR.Rdata')
   save(model.contrast4.genes_CVR, file = './models/model.contrast4.genes_CVR.Rdata')
   save(model.contrast4.behavior_CVR, file = './models/model.contrast4.behavior_CVR.Rdata')
   save(model.contrast4.brain_development_CVR, file = './models/model.contrast4.brain_development_CVR.Rdata')
```



#### (v) Univariate regression model - exercise timming

```{r exercise timming}
#***************************************************************#
#--------------------- Improvement (lnRR) ----------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model.contrast5.neuron_count_RR <- rma.mv(yi = RR, 
                                            V = cov_VRR_neuron_count, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                            data = neuron_count)


# brain_size
  model.contrast5.brain_size_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_brain_size, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                          data = brain_size)

# BDNF
  model.contrast5.BDNF_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_BDNF, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                    data = BDNF)

# TrkB
  model.contrast5.TrkB_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_TrkB, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                    data = TrkB)
# VEGF
  model.contrast5.VEGF_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_VEGF, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                    data = VEGF)
# reelin
  model.contrast5.reelin_RR <- rma.mv(yi = RR, 
                                      V = cov_VRR_reelin, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                      data = reelin)
# GFAP
  model.contrast5.GFAP_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_GFAP, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                    data = GFAP)
# syptophysin
  model.contrast5.syptophysin_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_syptophysin, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                           data = syptophysin)

# mitochondrial_biogenesis
  model.contrast5.mitochondrial_biogenesis_RR <- rma.mv(yi = RR, 
                                                        V = cov_VRR_mitochondrial_biogenesis, 
                                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                        mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                                        data = mitochondrial_biogenesis)
# DNA_methylation
  model.contrast5.DNA_methylation_RR <- rma.mv(yi = RR, 
                                               V = VRR, 
                                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                               mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                               data = DNA_methylation)
# learning_MWM
  model.contrast5.learning_MWM_RR <- rma.mv(yi = RR, 
                                            V = cov_VRR_learning_MWM, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                            data = learning_MWM)
# memory_MWM
  model.contrast5.memory_MWM_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_memory_MWM, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                          data = memory_MWM)
# memory_NOR
  model.contrast5.memory_NOR_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_memory_NOR, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                          data = memory_NOR)
# anxiety_OFT
  model.contrast5.anxiety_OFT_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_anxiety_OFT, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                           data = anxiety_OFT)
# anxiety_EPM
  model.contrast5.anxiety_EPM_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_anxiety_EPM, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                           data = anxiety_EPM)

#--------------------- Board traits----------------------#


# brain_development
  model.contrast5.brain_development_RR <- rma.mv(yi = RR, 
                                                 V = cov_VRR_brain_development, 
                                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                 mod = ~relevel(manipulation_window, ref = 'pre-conception'),
                                                 data = brain_development)


# genes
  model.contrast5.genes_RR <- rma.mv(yi = RR, 
                                     V = cov_VRR_genes, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(manipulation_window, ref = 'pre-conception'),
                                     data = genes)


# behavior
  model.contrast5.behavior_RR <- rma.mv(yi = RR, 
                                        V = cov_VRR_behavior, 
                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                        mod = ~relevel(manipulation_window, ref = 'pre-conception'),
                                        data = behavior)


#***************************************************************#
#------------------ Inter-individual differences (lnCVR) -------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model.contrast5.neuron_count_CVR <- rma.mv(yi = CVR, 
                                             V = cov_VCVR_neuron_count, 
                                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                             mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                             data = neuron_count)

# brain_size
  model.contrast5.brain_size_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_brain_size, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                           data = brain_size)

# BDNF
  model.contrast5.BDNF_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_BDNF, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                     data = BDNF)

# TrkB
  model.contrast5.TrkB_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_TrkB, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                    data = TrkB)
# VEGF
  model.contrast5.VEGF_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_VEGF, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                     data = VEGF)
# reelin
  model.contrast5.reelin_CVR <- rma.mv(yi = CVR, 
                                       V = cov_VCVR_reelin, 
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                       data = reelin)
# GFAP
  model.contrast5.GFAP_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_GFAP, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                     data = GFAP)
# syptophysin
  model.contrast5.syptophysin_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_syptophysin, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                            data = syptophysin)
# mitochondrial_biogenesis
  model.contrast5.mitochondrial_biogenesis_CVR <- rma.mv(yi = CVR, 
                                                         V = cov_VCVR_mitochondrial_biogenesis, 
                                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                         mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                                         data = mitochondrial_biogenesis)
# DNA_methylation
  model.contrast5.DNA_methylation_CVR <- rma.mv(yi = CVR, 
                                                V = VCVR, 
                                                random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                                data = DNA_methylation)
# learning_MWM
  model.contrast5.learning_MWM_CVR <- rma.mv(yi = CVR, 
                                             V = cov_VCVR_learning_MWM, 
                                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                             mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                             data = learning_MWM)
# memory_MWM
  model.contrast5.memory_MWM_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_memory_MWM, 
                                           random = list(~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                           data = memory_MWM)
# memory_NOR
  model.contrast5.memory_NOR_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_memory_NOR, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                           data = memory_NOR)
# anxiety_OFT
  model.contrast5.anxiety_OFT_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_anxiety_OFT, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                            data = anxiety_OFT)
# anxiety_EPM
  model.contrast5.anxiety_EPM_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_anxiety_EPM, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~relevel(manipulation_window, ref = 'pre-conception'), 
                                            data = anxiety_EPM)

#--------------------- Board traits----------------------#		

# brain_development
  model.contrast5.brain_development_CVR <- rma.mv(yi = CVR, 
                                                  V = cov_VCVR_brain_development, 
                                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                  mod = ~relevel(manipulation_window, ref = 'pre-conception'),
                                                  data = brain_development)	


# genes
  model.contrast5.genes_CVR <- rma.mv(yi = CVR, 
                                      V = cov_VCVR_genes, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~relevel(manipulation_window, ref = 'pre-conception'),
                                      data = genes)


# behavior
model.contrast5.behavior_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_behavior, 
                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~relevel(manipulation_window, ref = 'pre-conception'),
                                  data = behavior)	



# Saving models
 # Improvement (lnRR) 
   save(model.contrast5.neuron_count_RR, file = './models/model.contrast5.neuron_count_RR.Rdata')
   save(model.contrast5.brain_size_RR, file = './models/model.contrast5.brain_size_RR.Rdata')
   save(model.contrast5.BDNF_RR, file = './models/model.contrast5.BDNF_RR.Rdata')
   save(model.contrast5.TrkB_RR, file = './models/model.contrast5.TrkB_RR.Rdata')
   save(model.contrast5.VEGF_RR, file = './models/model.contrast5.VEGF_RR.Rdata')
   save(model.contrast5.reelin_RR, file = './models/model.contrast5.reelin_RR.Rdata')
   save(model.contrast5.GFAP_RR, file = './models/model.contrast5.GFAP_RR.Rdata')
   save(model.contrast5.syptophysin_RR, file = './models/model.contrast5.syptophysin_RR.Rdata')
   save(model.contrast5.mitochondrial_biogenesis_RR, file = './models/model.contrast5.mitochondrial_biogenesis_RR.Rdata')
   save(model.contrast5.DNA_methylation_RR, file = './models/model.contrast5.DNA_methylation_RR.Rdata')
   save(model.contrast5.learning_MWM_RR, file = './models/model.contrast5.learning_MWM_RR.Rdata')
   save(model.contrast5.memory_MWM_RR, file = './models/model.contrast5.memory_MWM_RR.Rdata')
   save(model.contrast5.memory_NOR_RR, file = './models/model.contrast5.memory_NOR_RR.Rdata')
   save(model.contrast5.anxiety_OFT_RR, file = './models/model.contrast5.anxiety_OFT_RR.Rdata')
   save(model.contrast5.anxiety_EPM_RR, file = './models/model.contrast5.anxiety_EPM_RR.Rdata')
   save(model.contrast5.genes_RR, file = './models/model.contrast5.genes_RR.Rdata')
   save(model.contrast5.behavior_RR, file = './models/model.contrast5.behavior_RR.Rdata')
   save(model.contrast5.brain_development_RR, file = './models/model.contrast5.brain_development_RR.Rdata')

 # Inter-individual differences (lnCVR) 
   save(model.contrast5.neuron_count_CVR, file = './models/model.contrast5.neuron_count_CVR.Rdata')
   save(model.contrast5.brain_size_CVR, file = './models/model.contrast5.brain_size_CVR.Rdata')
   save(model.contrast5.BDNF_CVR, file = './models/model.contrast5.BDNF_CVR.Rdata')
   save(model.contrast5.TrkB_CVR, file = './models/model.contrast5.TrkB_CVR.Rdata')
   save(model.contrast5.VEGF_CVR, file = './models/model.contrast5.VEGF_CVR.Rdata')
   save(model.contrast5.reelin_CVR, file = './models/model.contrast5.reelin_CVR.Rdata')
   save(model.contrast5.GFAP_CVR, file = './models/model.contrast5.GFAP_CVR.Rdata')
   save(model.contrast5.syptophysin_CVR, file = './models/model.contrast5.syptophysin_CVR.Rdata')
   save(model.contrast5.mitochondrial_biogenesis_CVR, file = './models/model.contrast5.mitochondrial_biogenesis_CVR.Rdata')
   save(model.contrast5.DNA_methylation_CVR, file = './models/model.contrast5.DNA_methylation_CVR.Rdata')
   save(model.contrast5.learning_MWM_CVR, file = './models/model.contrast5.learning_MWM_CVR.Rdata')
   save(model.contrast5.memory_MWM_CVR, file = './models/model.contrast5.memory_MWM_CVR.Rdata')
   save(model.contrast5.memory_NOR_CVR, file = './models/model.contrast5.memory_NOR_CVR.Rdata')
   save(model.contrast5.anxiety_OFT_CVR, file = './models/model.contrast5.anxiety_OFT_CVR.Rdata')
   save(model.contrast5.anxiety_EPM_CVR, file = './models/model.contrast5.anxiety_EPM_CVR.Rdata')
   save(model.contrast5.genes_CVR, file = './models/model.contrast5.genes_CVR.Rdata')
   save(model.contrast5.brain_development_CVR, file = './models/model.contrast5.brain_development_CVR.Rdata')
```




#### (vi) Univariate regression model - F1 ontogenetic stage

```{r F1 ontogenetic stage}
#***************************************************************#
#--------------------- improvement (lnRR) ----------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model.contrast6.neuron_count_RR <- rma.mv(yi = RR, 
                                            V = cov_VRR_neuron_count, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~response_age_life_phase, 
                                            data = neuron_count)

# brain_size
  model.contrast6.brain_size_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_brain_size, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~response_age_life_phase, 
                                          data = brain_size)

# BDNF
  model.contrast6.BDNF_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_BDNF, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~response_age_life_phase, 
                                    data = BDNF)

# TrkB
  model.contrast6.TrkB_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_TrkB, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~response_age_life_phase, 
                                    data = TrkB)
# VEGF
  model.contrast6.VEGF_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_VEGF, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~response_age_life_phase, 
                                    data = VEGF)
# reelin
  model.contrast6.reelin_RR <- rma.mv(yi = RR, 
                                      V = cov_VRR_reelin, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~response_age_life_phase, 
                                      data = reelin)
# GFAP
  model.contrast6.GFAP_RR <- rma.mv(yi = RR, 
                                    V = cov_VRR_GFAP, 
                                    random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                    mod = ~response_age_life_phase, 
                                    data = GFAP)
# syptophysin
  model.contrast6.syptophysin_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_syptophysin, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~response_age_life_phase, 
                                           data = syptophysin)
# mitochondrial_biogenesis
  model.contrast6.mitochondrial_biogenesis_RR <- rma.mv(yi = RR, 
                                                        V = VRR,#cov_VRR_mitochondrial_biogenesis, 
                                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                        mod = ~response_age_life_phase, 
                                                        data = mitochondrial_biogenesis)
# DNA_methylation
  model.contrast6.DNA_methylation_RR <- rma.mv(yi = RR, 
                                               V = VRR, 
                                               random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                               mod = ~response_age_life_phase, 
                                               data = DNA_methylation)
# learning_MWM
  model.contrast6.learning_MWM_RR <- rma.mv(yi = RR, 
                                            V = cov_VRR_learning_MWM, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~response_age_life_phase, 
                                            data = learning_MWM)
# memory_MWM
  model.contrast6.memory_MWM_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_memory_MWM, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~response_age_life_phase, 
                                          data = memory_MWM)
# memory_NOR
  model.contrast6.memory_NOR_RR <- rma.mv(yi = RR, 
                                          V = cov_VRR_memory_NOR, 
                                          random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                          mod = ~response_age_life_phase, 
                                          data = memory_NOR)
# anxiety_OFT
  model.contrast6.anxiety_OFT_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_anxiety_OFT, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~response_age_life_phase, 
                                           data = anxiety_OFT)
# anxiety_EPM
  model.contrast6.anxiety_EPM_RR <- rma.mv(yi = RR, 
                                           V = cov_VRR_anxiety_EPM, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~response_age_life_phase, 
                                           data = anxiety_EPM)

#--------------------- Board traits----------------------#

# genes
  model.contrast6.genes_RR <- rma.mv(yi = RR, 
                                     V = cov_VRR_genes, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~response_age_life_phase,
                                     data = genes)


# behavior
  model.contrast6.behavior_RR <- rma.mv(yi = RR, 
                                        V = cov_VRR_behavior, 
                                        random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                        mod = ~response_age_life_phase,
                                        data = behavior)

# brain_development
  model.contrast6.brain_development_RR <- rma.mv(yi = RR, 
                                                 V = cov_VRR_brain_development, 
                                                 random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                 mod = ~response_age_life_phase,
                                                 data = brain_development)


#***************************************************************#
#------------------ Inter-individual differences (lnCVR) -------------------#
#***************************************************************#


#--------------------- Separate traits----------------------#

# neuron count
  model.contrast6.neuron_count_CVR <- rma.mv(yi = CVR, 
                                             V = cov_VCVR_neuron_count, 
                                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                             mod = ~response_age_life_phase, 
                                             data = neuron_count)

# brain_size
  model.contrast6.brain_size_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_brain_size, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~response_age_life_phase, 
                                           data = brain_size)

# BDNF
  model.contrast6.BDNF_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_BDNF, 
                                     random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                     mod = ~response_age_life_phase, 
                                     data = BDNF)

# TrkB
  model.contrast6.TrkB_CVR <- rma.mv(yi = CVR, 
                                  V = cov_VCVR_TrkB, 
                                  random = list(~1|study_ID, ~1|ES_ID),
                                  mod = ~response_age_life_phase, 
                                  data = TrkB)
# VEGF
model.contrast6.VEGF_CVR <- rma.mv(yi = CVR, 
                                   V = cov_VCVR_VEGF, 
                                   random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                   mod = ~response_age_life_phase, 
                                   data = VEGF)
# reelin
  model.contrast6.reelin_CVR <- rma.mv(yi = CVR, 
                                       V = cov_VCVR_reelin, 
                                       random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                       mod = ~response_age_life_phase, 
                                       data = reelin)
# GFAP
  model.contrast6.GFAP_CVR <- rma.mv(yi = CVR, 
                                     V = cov_VCVR_GFAP, 
                                     random = list(~1|study_ID, ~1|ES_ID),
                                     mod = ~response_age_life_phase, 
                                     data = GFAP)
# syptophysin
  model.contrast6.syptophysin_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_syptophysin, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~response_age_life_phase, 
                                            data = syptophysin)
# mitochondrial_biogenesis
  model.contrast6.mitochondrial_biogenesis_CVR <- rma.mv(yi = CVR, 
                                                         V = cov_VCVR_mitochondrial_biogenesis, 
                                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                         mod = ~response_age_life_phase, 
                                                         data = mitochondrial_biogenesis)
# DNA_methylation
  model.contrast6.DNA_methylation_CVR <- rma.mv(yi = CVR, 
                                                V = VCVR, 
                                                random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                mod = ~response_age_life_phase, 
                                                data = DNA_methylation)
# learning_MWM
  model.contrast6.learning_MWM_CVR <- rma.mv(yi = CVR, 
                                             V = cov_VCVR_learning_MWM, 
                                             random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                             mod = ~response_age_life_phase, 
                                             data = learning_MWM)
# memory_MWM
  model.contrast6.memory_MWM_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_memory_MWM, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~response_age_life_phase, 
                                           data = memory_MWM)
# memory_NOR
  model.contrast6.memory_NOR_CVR <- rma.mv(yi = CVR, 
                                           V = cov_VCVR_memory_NOR, 
                                           random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                           mod = ~response_age_life_phase, 
                                           data = memory_NOR)
# anxiety_OFT
  model.contrast6.anxiety_OFT_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_anxiety_OFT, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~response_age_life_phase, 
                                            data = anxiety_OFT)
# anxiety_EPM
  model.contrast6.anxiety_EPM_CVR <- rma.mv(yi = CVR, 
                                            V = cov_VCVR_anxiety_EPM, 
                                            random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                            mod = ~response_age_life_phase, 
                                            data = anxiety_EPM)

#--------------------- Board traits----------------------#		

# genes
  model.contrast6.genes_CVR <- rma.mv(yi = CVR, 
                                      V = cov_VCVR_genes, 
                                      random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                      mod = ~response_age_life_phase,
                                      data = genes)


# behavior
  model.contrast6.behavior_CVR <- rma.mv(yi = CVR, 
                                         V = cov_VCVR_behavior, 
                                         random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                         mod = ~response_age_life_phase,
                                         data = behavior)

# brain_development
  model.contrast6.brain_development_CVR <- rma.mv(yi = CVR, 
                                                  V = cov_VCVR_brain_development, 
                                                  random = list(~1|strain, ~1|study_ID, ~1|ES_ID),
                                                  mod = ~response_age_life_phase,
                                                  data = brain_development)


# Saving models
 # Improvement (lnRR) 
   save(model.contrast6.neuron_count_RR, file = './models/model.contrast6.neuron_count_RR.Rdata')
   save(model.contrast6.brain_size_RR, file = './models/model.contrast6.brain_size_RR.Rdata')
   save(model.contrast6.BDNF_RR, file = './models/model.contrast6.BDNF_RR.Rdata')
   save(model.contrast6.TrkB_RR, file = './models/model.contrast6.TrkB_RR.Rdata')
   save(model.contrast6.VEGF_RR, file = './models/model.contrast6.VEGF_RR.Rdata')
   save(model.contrast6.reelin_RR, file = './models/model.contrast6.reelin_RR.Rdata')
   save(model.contrast6.GFAP_RR, file = './models/model.contrast6.GFAP_RR.Rdata')
   save(model.contrast6.syptophysin_RR, file = './models/model.contrast6.syptophysin_RR.Rdata')
   save(model.contrast6.mitochondrial_biogenesis_RR, file = './models/model.contrast6.mitochondrial_biogenesis_RR.Rdata')
   save(model.contrast6.DNA_methylation_RR, file = './models/model.contrast6.DNA_methylation_RR.Rdata')
   save(model.contrast6.learning_MWM_RR, file = './models/model.contrast6.learning_MWM_RR.Rdata')
   save(model.contrast6.memory_MWM_RR, file = './models/model.contrast6.memory_MWM_RR.Rdata')
   save(model.contrast6.memory_NOR_RR, file = './models/model.contrast6.memory_NOR_RR.Rdata')
   save(model.contrast6.anxiety_OFT_RR, file = './models/model.contrast6.anxiety_OFT_RR.Rdata')
   save(model.contrast6.anxiety_EPM_RR, file = './models/model.contrast6.anxiety_EPM_RR.Rdata')
   save(model.contrast6.genes_RR, file = './models/model.contrast6.genes_RR.Rdata')
   save(model.contrast6.behavior_RR, file = './models/model.contrast6.behavior_RR.Rdata')
   save(model.contrast6.brain_development_RR, file = './models/model.contrast6.brain_development_RR.Rdata')

 # Inter-individual differences (lnCVR) 
   save(model.contrast6.neuron_count_CVR, file = './models/model.contrast6.neuron_count_CVR.Rdata')
  save(model.contrast6.brain_size_CVR, file = './models/model.contrast6.brain_size_CVR.Rdata')
   save(model.contrast6.BDNF_CVR, file = './models/model.contrast6.BDNF_CVR.Rdata')
   save(model.contrast6.TrkB_CVR, file = './models/model.contrast6.TrkB_CVR.Rdata')
   save(model.contrast6.VEGF_CVR, file = './models/model.contrast6.VEGF_CVR.Rdata')
   save(model.contrast6.reelin_CVR, file = './models/model.contrast6.reelin_CVR.Rdata')
   save(model.contrast6.GFAP_CVR, file = './models/model.contrast6.GFAP_CVR.Rdata')
   save(model.contrast6.syptophysin_CVR, file = './models/model.contrast6.syptophysin_CVR.Rdata')
   save(model.contrast6.mitochondrial_biogenesis_CVR, file = './models/model.contrast6.mitochondrial_biogenesis_CVR.Rdata')
   save(model.contrast6.DNA_methylation_CVR, file = './models/model.contrast6.DNA_methylation_CVR.Rdata')
   save(model.contrast6.learning_MWM_CVR, file = './models/model.contrast6.learning_MWM_CVR.Rdata')
   save(model.contrast6.memory_MWM_CVR, file = './models/model.contrast6.memory_MWM_CVR.Rdata')
   save(model.contrast6.memory_NOR_CVR, file = './models/model.contrast6.memory_NOR_CVR.Rdata')
   save(model.contrast6.anxiety_OFT_CVR, file = './models/model.contrast6.anxiety_OFT_CVR.Rdata')
   save(model.contrast6.anxiety_EPM_CVR, file = './models/model.contrast6.anxiety_EPM_CVR.Rdata')
   save(model.contrast6.genes_CVR, file = './models/model.contrast6.genes_CVR.Rdata')
   save(model.contrast6.behavior_CVR, file = './models/model.contrast6.behavior_CVR.Rdata')
   save(model.contrast6.brain_development_CVR, file = './models/model.contrast6.brain_development_CVR.Rdata')
```
